### 2016-01-21 chapters/abstract.tex
initial commit with first draft layout

In diesem Paper soll beschrieben werden, wie die Generierung eines Feature-Modells aus der Ordnerstruktur und den Konfigurationsdateien einer Produktlinie vorgenommen wird, hier am Beispiel von odoo.
Weiterhin wird der Vorgang der Konfiguration von Produktlinien betrachtet. Dazu wird zun\"achst untersucht, welche bestehenden Verfahren verwendet werden und ein Konzept, aufbauend auf dem Prinzip eines Fragebogens, entwickelt. Dabei soll auch die Erstellung eines solchen Fragebogens und die Beachtung einer eventuell gew\"unschten Reihenfolge in die Entwicklung des Konzeptes einflie\ss en.
Abschlie\ss end wird eine beispielhafte Umsetzung dieses Konzeptes in der IDE \textit{featureIDE} mit den zuvor ermittelten Anforderungen abgeglichen und bewertet.

### 2016-01-21 chapters/background.tex
initial commit with first draft layout

Aktueller Stand der Technik, Beispiele, Vergleich der bestehenden Methoden, gemeinsame Schw\"achen finden

### 2016-01-21 chapters/concept.tex
initial commit with first draft layout

Schrittweise die Idee entwickeln und L\"osungswege f\"ur die gegebenen Probleme finden. Insbesondere auch verschiedene Ans\"atze vergleichen und getroffene Entscheidungen begr\"unden.

### 2016-01-21 chapters/conclusion.tex
initial commit with first draft layout

\subsection{Zusammenfassung}
Hier gibt es eine Zusammenfassung, der Arbeit. Darin flie\ss t insbesondere der gegangene Weg und die erlangten Erfahrungen ein. Insbesondere die gewonnenen Erkenntnisse in dieser Arbeit werden hervorgehoben und die Bewertung des entwickelten Konzeptes in wenigen S\"atzen zusammengefasst.

\subsection{Ausblick}
Hier werden die Fragen, die im Rahmen dieser Arbeit aufgeworfen wurden, konkretisiert und Themen f\"ur weitergehende Untersuchungen aufgez\"ahlt. Insbesondere Probleme, die das entwickelte Konzept nicht l\"osen kann sollen hervorgehoben werden (und warum) und erste Ans\"atze zu deren L\"osung vorgeschlagen werden.

### 2016-01-21 chapters/intro.tex
initial commit with first draft layout

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{F}{eature} Modell sind als Werkzeug f\"ur Produktilinien unverzichtbar. Daher sollen sie in dieser Arbeit automatisch generiert werden, aus Konventionen, die in dem Projekt KONSEQUENT *hust* umgesetzt wurden.
Auch die Konfiguration ist ein elementarer Bestandteil der Arbeit mit Produktlinien, daher soll auch sie in dieser Arbeit Beachtung finden. Dazu werden zun\"achst bestehende Methoden betrachtet und miteinander verglichen. Dem wird ein neuer Ansatz basierend auf Frageb\"ogen gegen\"ubergestellt. F\"ur diesen Ansatz werden zun\"achst die Anforderungen an ein Konfigurationssystem ermittelt. Auch werden die zu erreichenden Verbesserungen gegen\"uber den bestehenden Systemen vorgestellt, inbesondere im Bereich der \textit{Usability}. Anhand von vorangegangenen Untersuchungen zur Struktur von Frageb\"ogen wird anschlie\ss end ein Konzept entwickelt, das es Spezialisten erlaubt, ihre Dom\"anenkenntnisse in die Konfiguration einflie\ss en zu lassen, insbesondere in Bezug auf die Reihenfolge der zu treffenden Entscheidungen im Rahmen einer Konfiguration einer Produktlinie.

Abschlie\ss end wird das erarbeitete Konzept anhand einer beispielhaften Implementierung in die \textit{featureIDE} untersucht und insbesondere unter Anbetracht der eingangs ermittelten Anforderungen bewertet.

### 2016-01-21 chapters/intro.tex
restructuring and beginning to use english language

@@
 % and "HIS" in caps to complete the first word.
-\IEEEPARstart{F}{eature} Modell sind als Werkzeug f\"ur Produktilinien unverzichtbar.
-Daher sollen sie in dieser Arbeit automatisch generiert werden, aus Konventionen, die in dem Projekt KONSEQUENT *hust* umgesetzt wurden.
-Auch die Konfiguration ist ein elementarer Bestandteil der Arbeit mit Produktlinien, daher soll auch sie in dieser Arbeit Beachtung finden.
-Dazu werden zun\"achst bestehende Methoden betrachtet und miteinander verglichen.
-Dem wird ein neuer Ansatz basierend auf Frageb\"ogen gegen\"ubergestellt.
-F\"ur diesen Ansatz werden zun\"achst die Anforderungen an ein Konfigurationssystem ermittelt.
-Auch werden die zu erreichenden Verbesserungen gegen\"uber den bestehenden Systemen vorgestellt, inbesondere im Bereich der \textit{Usability}.
+\IEEEPARstart{C}{onfiguration} is an essential part of working on product lines.
+This paper considers existing methods of configuration and tries to come up with a better alternative based on an approach with surveys.
+Feature Models are vital tools for the configuration of product lines.
+This work aims at automatically generating feature models out of descriptive files and naming conventions, to simplify a big part of the configuration.
+
 Anhand von vorangegangenen Untersuchungen zur Struktur von Frageb\"ogen wird anschlie\ss end ein Konzept entwickelt, das es Spezialisten erlaubt, ihre Dom\"anenkenntnisse in die Konfiguration einflie\ss en zu lassen, insbesondere in Bezug auf die Reihenfolge der zu treffenden Entscheidungen im Rahmen einer Konfiguration einer Produktlinie.
@@
 Abschlie\ss end wird das erarbeitete Konzept anhand einer beispielhaften Implementierung in die \textit{featureIDE} untersucht und insbesondere unter Anbetracht der eingangs ermittelten Anforderungen bewertet.
+
+Contribution
+
+Simplifying the process of configuration of productlines in FeatureIDE

### 2016-02-03 chapters/abstract.tex
restructuring and changing for english style. starting to include a bibliography for references

@@
-In diesem Paper soll beschrieben werden, wie die Generierung eines Feature-Modells aus der Ordnerstruktur und den Konfigurationsdateien einer Produktlinie vorgenommen wird, hier am Beispiel von odoo.
-Weiterhin wird der Vorgang der Konfiguration von Produktlinien betrachtet.
-Dazu wird zun\"achst untersucht, welche bestehenden Verfahren verwendet werden und ein Konzept, aufbauend auf dem Prinzip eines Fragebogens, entwickelt.
-Dabei soll auch die Erstellung eines solchen Fragebogens und die Beachtung einer eventuell gew\"unschten Reihenfolge in die Entwicklung des Konzeptes einflie\ss en.
-Abschlie\ss end wird eine beispielhafte Umsetzung dieses Konzeptes in der IDE \textit{featureIDE} mit den zuvor ermittelten Anforderungen abgeglichen und bewertet.
+Variability management is an essential part of working on product lines.
+This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
+To further simplify the process of product configuration out of software product-lines, feature models are used to describe the set of features and constraints contained in a given software product-line.
+This paper proposes a method for automatically generating feature models out of descriptive files and naming conventions.

### 2016-02-03 chapters/concept.tex
restructuring and changing for english style. starting to include a bibliography for references

@@
-Schrittweise die Idee entwickeln und L\"osungswege f\"ur die gegebenen Probleme finden. Insbesondere auch verschiedene Ans\"atze vergleichen und getroffene Entscheidungen begr\"unden.
+\subsection{Problem statement}
+Very high complexity of configuration due to many features and constraints.
+Domain knowledge is highly required to understand the given software product-line and being able to combine it's features to a valid configuration which satisfies the users needs.
+
+\subsection{State of the art}
+Compare the existing approaches to the stated problem and show why they are insufficient.
+
+\subsection{Questionnaire Approach}
+Use benefits of the existing approaches and overcome their shortcomings to solve the problem. State different variants and show the best one through comparison.

### 2016-02-03 chapters/conclusion.tex
restructuring and changing for english style. starting to include a bibliography for references

@@
-\subsection{Zusammenfassung}
-Hier gibt es eine Zusammenfassung, der Arbeit.
-Darin flie\ss t insbesondere der gegangene Weg und die erlangten Erfahrungen ein.
-Insbesondere die gewonnenen Erkenntnisse in dieser Arbeit werden hervorgehoben und die Bewertung des entwickelten Konzeptes in wenigen S\"atzen zusammengefasst.
+\subsection{Conclusion}
+This is where the work is concluded.
+In this section there will be a description of the way we did things and the experiences we made during it.
+An emphasis will be on the insights and the findings from the scenarios will get outlined.
 
-\subsection{Ausblick}
-Hier werden die Fragen, die im Rahmen dieser Arbeit aufgeworfen wurden, konkretisiert und Themen f\"ur weitergehende Untersuchungen aufgez\"ahlt.
-Insbesondere Probleme, die das entwickelte Konzept nicht l\"osen kann sollen hervorgehoben werden (und warum) und erste Ans\"atze zu deren L\"osung vorgeschlagen werden.
+\subsection{Future Work}
+Here will be a summary of the new questions that were raised in this work.
+Also there will be topics for further research.
+Particularly the problems we encountered and couldn't solve with our concept and why will be pointed out and first approaches will be suggested.

### 2016-02-03 chapters/intro.tex
restructuring and changing for english style. starting to include a bibliography for references

@@
 % and "HIS" in caps to complete the first word.
-\IEEEPARstart{C}{onfiguration} is an essential part of working on product lines.
-This paper considers existing methods of configuration and tries to come up with a better alternative based on an approach with surveys.
-Feature Models are vital tools for the configuration of product lines.
+\IEEEPARstart{V}{ariability} management is an essential part of working on product lines.
+There are several approaches trying to control the vast amount of product variants though configuration.
+This allows experts to apply their domain knowledge in order to a resulting product conforming to a users needs.
+
+This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
+
+Feature Models are vital tools for the configuration of product lines in such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line.
 This work aims at automatically generating feature models out of descriptive files and naming conventions, to simplify a big part of the configuration.
 
-Anhand von vorangegangenen Untersuchungen zur Struktur von Frageb\"ogen wird anschlie\ss end ein Konzept entwickelt, das es Spezialisten erlaubt, ihre Dom\"anenkenntnisse in die Konfiguration einflie\ss en zu lassen, insbesondere in Bezug auf die Reihenfolge der zu treffenden Entscheidungen im Rahmen einer Konfiguration einer Produktlinie.
-
-Abschlie\ss end wird das erarbeitete Konzept anhand einer beispielhaften Implementierung in die \textit{featureIDE} untersucht und insbesondere unter Anbetracht der eingangs ermittelten Anforderungen bewertet.
-
-Contribution
+\section*{Contribution}
 
 Simplifying the process of configuration of productlines in FeatureIDE
+
+This\cite{fpe} is\cite{qdc} a\cite{qbvm} dummy to create citations.

### 2016-02-03 chapters/scenarios.tex
restructuring and changing for english style. starting to include a bibliography for references

State a few usage scenarios and show why the questionnaire is better or as good as the existing solutions. Also point out in which scenario this might be the wrong tool.

### 2016-02-11 chapters/concept.tex
slight restructuring

--- 2016-01-21 chapters/concept.tex
@@
-Schrittweise die Idee entwickeln und L\"osungswege f\"ur die gegebenen Probleme finden. Insbesondere auch verschiedene Ans\"atze vergleichen und getroffene Entscheidungen begr\"unden.
+General workflow Diagram
+
+unstructured product line $\rightarrow$ generated feature model $\rightarrow$ optimizing (via SAT-solver?) $\rightarrow$ domain knowledge of an expert $\Rightarrow$ Questionnaire $\rightarrow$ Feature model + Questionnaire $\Rightarrow$ Product (variant)
+
+\subsection{Extraction of a feature model}
+Describe the conventions and which rules are applied to generate a feature model out of it.
+
+\subsection{Questionnaire Approach}
+Use benefits of the existing approaches and overcome their shortcomings to solve the problem. State different variants and show the best one through comparison.

### 2016-02-11 chapters/intro.tex
slight restructuring

@@
 
-This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
-
 Feature Models are vital tools for the configuration of product lines in such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line.
@@
 
+This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
+
+\section*{Problem statement}
+Very high complexity of configuration due to many features and constraints.
+Domain knowledge is highly required to understand the given software product-line and being able to combine it's features to a valid configuration which satisfies the users needs.
+
 \section*{Contribution}
 
-Simplifying the process of configuration of productlines in FeatureIDE
+Simplifying the process of configuration of product lines through extracting a feature model out of naming conventions and configuration files from an existing product line in FeatureIDE and applying a configuration wizard which guides the user though the creation of a specific product (variant) in the style of a questionnaire, thus applying the domain knowledge of an expert.
 
-This\cite{fpe} is\cite{qdc} a\cite{qbvm} dummy to create citations.
+This\cite{fpe} is\cite{qdc} a\cite{qbvm} dummy\cite{fmgp} to create citations.

### 2016-02-12 chapters/abstract.tex
short notes for each section

@@
 Variability management is an essential part of working on product lines.
-This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
-To further simplify the process of product configuration out of software product-lines, feature models are used to describe the set of features and constraints contained in a given software product-line.
+As an established way to simplify the process of product configuration out of software product-lines, feature models are used to describe the set of features and constraints contained in a given software product-line.
 This paper proposes a method for automatically generating feature models out of descriptive files and naming conventions.
+Furthermore existing methods of configuration are considered in this work and to develop an alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.

### 2016-02-12 chapters/background.tex
restructuring and changing for english style. starting to include a bibliography for references
slight restructuring
short notes for each section

@@
-Aktueller Stand der Technik, Beispiele, Vergleich der bestehenden Methoden, gemeinsame Schw\"achen finden
+\subsection{Feature Models}
+Multi-purpose tool for product lines:
+\begin{itemize}
+\item Visualization of the possible features and their hierarchy
+\item Classification of features and their dependencies (alternative/or; optional/mandatory/abstract)
+\item Formal Representation of the whole product line $\Rightarrow$ computationally processable
+\item assistance/foundation for configuration and variant validation
+\end{itemize}
+
+\subsection{Product configuration}
+Customizing a product line to specific needs, resulting in a product/variant\\
+Simplified to a list of (un-)selected features contained in the resulting product/variant\\
+
+\subsection{Constraints, contradictions, SAT-solver}
+Rules \& constraints specify (in-)valid configurations $\Rightarrow$ formalism of feature models allows SAT-solvers to check for validity\\
+Already possible after each step of the ongoing configuration to check partial configurations

### 2016-02-12 chapters/concept.tex
short notes for each section

@@
 \subsection{Extraction of a feature model}
-Describe the conventions and which rules are applied to generate a feature model out of it.
+The (Naming-)conventions and rules that are applied to generate a feature model out of it.\\
+State the problems? Error-Handling on failure to comply the conventions?
 
 \subsection{Questionnaire Approach}
-Use benefits of the existing approaches and overcome their shortcomings to solve the problem. State different variants and show the best one through comparison.
+Use questions to guide the user through a conditional configuration process.
+The questions, their order and the influences of the answers are pre-defined by a developer/an expert who uses his domain knowledge to design the questionnaire.
+Therefore, a data structure is introduced and mapped to a specific set of XML-tags.

### 2016-02-12 chapters/intro.tex
short notes for each section

@@
 % and "HIS" in caps to complete the first word.
-\IEEEPARstart{V}{ariability} management is an essential part of working on product lines.
+\IEEEPARstart{S}{oftware} product lines.
+foo.
 There are several approaches trying to control the vast amount of product variants though configuration.
@@
 
-Feature Models are vital tools for the configuration of product lines in such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line.
+Feature Models are essential tools for the configuration of product lines in such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line.
 This work aims at automatically generating feature models out of descriptive files and naming conventions, to simplify a big part of the configuration.

### 2016-02-17 chapters/background.tex
first textual variant for the 'basics' section

--- 2016-01-21 chapters/background.tex
@@
-Aktueller Stand der Technik, Beispiele, Vergleich der bestehenden Methoden, gemeinsame Schw\"achen finden
+In the scope of simplifying the configuration of a given product line some specific tools and techniques were used.
+This section will give an overview of what was used in this work to archive the simplification.
+
+\subsection{Feature Models}
+Feature models are multi-purpose tool for product lines. Figure~\ref{img-fm} shows a simplified example of a feature model.
+\begin{figure}
+	\includegraphics{img/img-fm.png}
+	\caption{A simple example of a feature model}
+	\label{img-fm}
+\end{figure}
+Amongst their benefits are:
+\begin{itemize}
+\item Visualization of the possible features and their hierarchy
+\item Classification of features and their dependencies (alternative/or; optional/mandatory/abstract)
+\item Formal Representation of the whole product line $\Rightarrow$ computationally processable
+\item Assistance/foundation for configuration and variant validation
+\end{itemize}
+They are basically structured like trees: There is a root node, an arbitrary number of levels of nodes and finally leaf nodes without child nodes of their own.
+In that manner feature models map the hierarchy of features.
+In addition they mark each feature as either mandatory or optional as well as either abstract or concrete.
+The possible relationships of multiple features with a mutual parent feature are \textit{or} (at least one feature has to be selected), \textit{alternative} (exactly one feature has to be selected) and \textit{and} (any number of features can be selected).
+As features' relations may be of higher complexity than just parent-child relations additional constraints can be noted within a feature model.
+Constraints are boolean expressions, the example in figure~\ref{img-fm} shows an implication.
+
+\subsection{Product configuration}
+Through configuration a concrete product can be derived from a product line. Each valid configuration represents a specific \textit{variant} of the possible products.
+
+During configuration a user selects or unselects features to his needs.
+This process requires a lot of domain knowledge on the one hand and detailed information about each single feature on the other.
+With growing numbers of possible features (and thus growing numbers of possible variants) configuration get more and more complex and turns out to be not trivial.
+
+One of the purposes of the feature-oriented approach is saving the effort of creating a whole new product and deriving that product from a product line instead.
+The sheer overhead of configuration might even negate that benefit if configuration grows too complex.
+
+\subsection{Constraints, contradictions, SAT-solver}
+As stated above a feature model may contain constraints in the form of boolean expressions.
+Also, the feature-tree can be expressed as a boolean statement.
+The model shown in figure~\ref{img-fm} can be expressed as follows:
+\begin{equation}
+\begin{split}
+	GraphLibrary\ \wedge\ Edges\\
+	\wedge\ ((Directed\ \wedge \neg Undirected)\\
+	\vee (\neg Directed\ \wedge\ Undirected))\\
+	\wedge\ (Algorithms\ \Rightarrow\ (Number\ \vee\ Cycle))\\
+	\wedge\ (Cycle\ \Rightarrow\ Directed)
+\end{split}
+\end{equation}\\
+This formalism allows a configuration to be checked for validity.
+To do so each selected Feature is appended with a logical \textit{AND} and each specifically unselected feature is also appended with a logical \textit{AND} but gets negated.
+The resulting expression is then evaluated by a SAT-solver to check for satisfiability.
+Even during configuration this process can be applied to check for invalid partial configurations after each decision.

### 2016-03-01 chapters/concept.tex
general description of the workflow and explanation of the used conventions

@@
-General workflow Diagram
+[Diagram showing the general workflow]
 
-unstructured product line $\rightarrow$ generated feature model $\rightarrow$ optimizing (via SAT-solver?) $\rightarrow$ domain knowledge of an expert $\Rightarrow$ Questionnaire $\rightarrow$ Feature model + Questionnaire $\Rightarrow$ Product (variant)
+unstructured product line $\rightarrow$ generated feature model $\rightarrow$ optimizing (via SAT-solver?) $\rightarrow$ domain knowledge of an expert $\Rightarrow$ Questionnaire $\rightarrow$ Feature model + Questionnaire $\Rightarrow$ Product (variant)\\
+
+Figure~\ref{img-workflow} shows the general process aimed to archive within this work.
+At the beginning there is only a given product line with the modular code artifacts in their specific subdirectories of the project.
+These code artifacts follow certain conventions to describe their integration in the context of the whole project.
+
+Using these conventions a feature model gets extracted in which the hierarchies and dependencies of the code artifacts are included.
+This allows for much better overview or automated optimization, for example scanning for dead features via SAT-solver.
+The extracted feature model will also be used in the following step of configuration.
+
+Configuration of product lines generally requires a good understanding of the given problems and the possible solutions to these problems as well as the specific implementations of these solutions.
+This domain knowledge is the most challenging part of configurations and restricts most of the possible users to do the configuration on their own.
+
+To transfer the domain knowledge of experts to the product line a questionnaire is introduced.
+In the progress of implementing the product line experts also design a questionnaire in such a way that a possible user has to answer a given amount of questions to perform the configuration of a variant meeting his personal needs without him having to know all the details of the implementation of the product line or even the individual features.
+The two major steps of extraction and the creation and usage of the questionnaire are described in detail on the following sections.
 
 \subsection{Extraction of a feature model}
-The (Naming-)conventions and rules that are applied to generate a feature model out of it.\\
-State the problems? Error-Handling on failure to comply the conventions?
+To automatically extract a feature model out of a given software project the structure of that project must be algorithmically understandable.
+To archive this, conventions are used for the project of which an overview follows:
+
+\begin{itemize}
+	\item All features are stored within a specified directory
+	\item Each feature is stored in a separate directory
+	\item A feature's parent features are stated in the name of the corresponding directory
+	\begin{itemize}
+		\item The complete hierarchy is displayed, except for the root feature
+		\item Individual parent features are delimited with an unique symbol
+	\end{itemize}
+	\item Each feature directory contains a configuration file with a specified name containing:
+	\begin{itemize}
+		\item A descriptive name of the feature
+		\item A description text for the feature
+		\item All dependencies including the parent features
+	\end{itemize}
+\end{itemize}
+
+All of these information are included in the resulting feature model.
+The most obvious correspondence lies within the hierarchy.
+The parent names are parsed from the directory name and -if existing- looked up in the existing partial feature model from the previously parsed features.
+As the directories are parsed in alphabetical order a parent feature will always be processed before it's child features.
+
+After placing it in the correct position within the existing partial feature model each feature's configuration file gets processed.
+Each feature gets enriched with it's descriptive details and it's dependencies.
+The list of dependencies firstly gets reduced by the parent features as the feature models hierarchy already implements this kind of dependencies.
+The remaining dependencies are stated as constraints.
+To shorten the list of constraints shared dependencies between multiple features are combined to a single constraint.\\
+
+{\color{red}TODO: State the problems:
+\begin{itemize}
+\item Error-Handling on failure to comply the conventions
+\item Missing Parent Features $\rightarrow$ Abstract features (can be configured beforehand)
+\end{itemize}}
 

### 2016-03-09 chapters/concept.tex
added questinnaire approach

@@
 \subsection{Extraction of a feature model}
-To automatically extract a feature model out of a given software project the structure of that project must be algorithmically understandable.
+To automatically extract a feature model out of a given software project the structure of that project must be algorithmically processable.
 To archive this, conventions are used for the project of which an overview follows:
@@
 \subsection{Questionnaire Approach}
-Use questions to guide the user through a conditional configuration process.
-The questions, their order and the influences of the answers are pre-defined by a developer/an expert who uses his domain knowledge to design the questionnaire.
-Therefore, a data structure is introduced and mapped to a specific set of XML-tags.
+As stated above configuration is one of the most challenging tasks within the scope of software product lines.
+In the previous section the automatic extraction of a feature model out of existing source code was explained.
+The resulting feature model yields a much better overview over the possible features and their interrelationships.
+Although the formalism of a feature model allows for tool support to simplify the process of configuration, still a lot of domain knowledge is required to be able to find the right combination of features for a given use-case.
+
+This work therefore introduces a method to allow experts to apply their knowledge and understanding to a whole product line during the development and thus enabling end users to draw on this knowledge whenever a configuration is taking place.
+
+In this work we made the decision to use a questionnaire based approach.
+Depending on the implementation of the questionnaire during development a partial or event complete configuration can be archived by a user through just answering the questions of the questionnaire.
+The concrete selection of features gets lifted to a higher level of abstraction.
+The user only has to decide between the possible answers presented to him in the questionnaire to best fit to his use-case.
+Internally the selected answers are mapped to a specified (un-)selection of features so the user avoids the hassle of considering implementation-details of each feature.
+
+This highly depends on the implementation of the questionnaire during development.
+Our work therefore introduces a set of tools to easily integrate such a questionnaire.
+The following paragraphs will give an overview over the the possible definitions of a questionnaire.
+
+Each page of the questionnaire is defined independently.
+It always contains at least a Question and more then one possible answer.
+The answers can be grouped analogous to the grouping of features in a feature model: \textit{OR} (at least one answer has to be selected), \textit{ALTERNATIVE} (exactly one answer has to be selected) and \textit{AND} (any number of answers can be selected).
+
+Each answer internally has a mapping to a set of features. This set of features defines which features are selected or specifically unselected in the case of that answer being chosen by the user.
+
+Each answer can also have an indicator to define which page of the questionnaire is to be displayed next.
+An answer can also indicate the end of the questionnaire.
+If no next page is defined the questionnaire will continue with the next page within it's definition.
+This allows a dynamic conditional design of the questionnaire so the user is only confronted with the exact set of questions needed to configure the variant for his specific use-case.
+This also allows the user to skip questions or cancel the configuration before finishing it and thus creating a partial configuration.
+
+In this work we also introduce a data structure to hold the definition of a questionnaire.
+To archive easy integration we decided for a definition in XML.
+We defined the necessary tags to create a questionnaire which are displayed in the following code snippet:
+
+\begin{lstlisting}
+<configurationSurvey>
+	<projectName>Name</projectName>
+	<section id="0">
+		<name>Section Name</name>
+		<description>Section description</description>
+	</section>
+	<page id="0" sectionId="0">
+		<question>Question for the user</question>
+		<answers type="alternative">
+			<answer nextPageId="1">
+				<label>Answer label</label>
+				<description>Answer description</description>
+				<dependencies>
+					<feature selection="false">Unselected feature</feature>
+					<feature>selected feature</feature>
+				</dependencies>
+			</answer>
+		</answers>
+	</page>
+</configurationSurvey>
+\end{lstlisting}
+
+\begin{tabular}{ l | l | l }
+\textbf{Tag} & \textbf{attributes} & \textbf{child tags}\\
+\hline
+\hline
+configurationSurvey & & projectName, section, page\\
+\hline
+section & id & name, description\\
+\hline
+page & id, sectionId & question, answers\\
+\hline
+answers & type & answer\\
+\hline
+answer & nextPageId & label, description, dependencies\\
+\hline
+dependencies & & feature\\
+\hline
+feature & selection & \\
+\end{tabular}\\
+
+The individual tags are explained as follows:
+
+\begin{itemize}
+\item configurationSurvey: The root tag to contain all other tags for the questionnaire.
+\item section: Enables grouping of question-pages. Also displays the name and description at the top of every page.
+\item page: Contains a question and the corresponding answers. Also has an indicator for a section
+\item answers: Contains the individual possible answers and groups them in the specified manner.
+\item answer: Defines the displayed text of an answer as well as the corresponding features. Can also have an indicator for the next page.
+\item dependencies: Defines the (un-)selection of features, if the corresponding answer gets selected.
+\end{itemize}

### 2016-03-10 chapters/background.tex

@@
 In addition they mark each feature as either mandatory or optional as well as either abstract or concrete.
-The possible relationships of multiple features with a mutual parent feature are \textit{or} (at least one feature has to be selected), \textit{alternative} (exactly one feature has to be selected) and \textit{and} (any number of features can be selected).
+The possible relationships of multiple features with a mutual parent feature are \textit{OR} (at least one feature has to be selected), \textit{ALTERNATIVE} (exactly one feature has to be selected) and \textit{AND} (any number of features can be selected).
 As features' relations may be of higher complexity than just parent-child relations additional constraints can be noted within a feature model.

### 2016-03-10 chapters/intro.tex
added questinnaire approach
Nochmal geändert!

@@
 % and "HIS" in caps to complete the first word.
-\IEEEPARstart{S}{oftware} product lines.
-foo.
-There are several approaches trying to control the vast amount of product variants though configuration.
-This allows experts to apply their domain knowledge in order to a resulting product conforming to a users needs.
+\IEEEPARstart{D}{eveloping} software product lines can result in a great amount of variants, when customizing the Software to each customers needs.
+By developing with a feature-oriented approach the configuration of a single variant can be done by selecting the features a customer needs, automatically including its dependencies.
+The configuration is based on a Feature Model, that defines the available Features and its relations to one another.
 
-Feature Models are essential tools for the configuration of product lines in such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line.
-This work aims at automatically generating feature models out of descriptive files and naming conventions, to simplify a big part of the configuration.
+Feature Models are essential structures for the feature-oriented development and later configuration of software product lines (SPL).
+In such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line.
+There are projects being developed feature-oriented, but don't have a feature model yet.
+This work aims at automatically generating it out of descriptive files and naming conventions, to simplify a big part of the feature model creation.
+
+Although the feature configuration gives  Developers the ability to create custom variants, there still has to be a consultant explaining the features to the customer, trying to figure out his current and future needs.
+As the Software grows and gets more features, this process gets more difficult, as you can no longer explain all the features, but you still have to figure out if the customer needs them or not.
 
@@
 
-This\cite{fpe} is\cite{qdc} a\cite{qbvm} dummy\cite{fmgp} to create citations.
+%This\cite{fpe} is\cite{qdc} a\cite{qbvm} dummy\cite{fmgp} to create citations.

### 2016-03-15 chapters/intro.tex
Arbeit an der Introduction

@@
 There are projects being developed feature-oriented, but don't have a feature model yet.
+Implementing it on top of a given Project can result in a very complex task due to the amount of its features and the constraints between them.
+Additionally those informations are often already kept inside of readme- or configuration files, what predesignates it to be analyzed programmatically.
 This work aims at automatically generating it out of descriptive files and naming conventions, to simplify a big part of the feature model creation.
@@
 As the Software grows and gets more features, this process gets more difficult, as you can no longer explain all the features, but you still have to figure out if the customer needs them or not.
-
 This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
 
-\section*{Problem statement}
-Very high complexity of configuration due to many features and constraints.
-Domain knowledge is highly required to understand the given software product-line and being able to combine it's features to a valid configuration which satisfies the users needs.
+FeatureIDE being the leading open source IDE for feature-oriented-software development, it provides us with all the functionality needed to programatically generate and work with Feature Models.
+The underlying Eclipse enables us to implement the feature extraction and the questionnaire as a plugin.
 
-\section*{Contribution}
+This work will demonstrate the named simplifications based on a real life Project.
+This software, an open source ERP System called "Odoo" [] is predestined to be developed feature-oriented due to a huge amount of features and complex constraints.
+The Project is currently being developed and structured feature oriented, although it doest't contain a Feature Model yet.
+Furthermore Odoo reached a critical amount of features where a salesman cannot consult a customer by going through all of the features anymore, but has to come up with a more effective way.
 
-Simplifying the process of configuration of product lines through extracting a feature model out of naming conventions and configuration files from an existing product line in FeatureIDE and applying a configuration wizard which guides the user though the creation of a specific product (variant) in the style of a questionnaire, thus applying the domain knowledge of an expert.
-
-%This\cite{fpe} is\cite{qdc} a\cite{qbvm} dummy\cite{fmgp} to create citations.
+The paper is structured as follows. In section 2 we ... . Followed by section 3 where we ... . Then in section 4, ... . Finally we conclude and give an outlook for future works.

### 2016-03-15 chapters/background.tex
Kapitel 2 Teil A korrigiert

@@
 \subsection{Feature Models}
-Feature models are multi-purpose tool for product lines. Figure~\ref{img-fm} shows a simplified example of a feature model.
+Feature models are multi-purpose structure for product lines. 
 \begin{figure}
@@
 \begin{itemize}
-\item Visualization of the possible features and their hierarchy
+\item Can be visualized as a feature diagram, showing the possible features and their hierarchy
 \item Classification of features and their dependencies (alternative/or; optional/mandatory/abstract)
-\item Formal Representation of the whole product line $\Rightarrow$ computationally processable
-\item Assistance/foundation for configuration and variant validation
+\item Formal Representation of the whole product line as a feature diagram $\Rightarrow$ computationally processable
+\item Enables configuration and variant validation
 \end{itemize}
-They are basically structured like trees: There is a root node, an arbitrary number of levels of nodes and finally leaf nodes without child nodes of their own.
+Although feature models can be represented as a boolean formula in CNF or grammer (GUIDSL), it is typically represented in form of a feature diagram and constraints.
+The feature diagram is basically structured as a tree: There is a root node, an arbitrary number of levels of nodes and finally leaf nodes without child nodes of their own.
 In that manner feature models map the hierarchy of features.
-In addition they mark each feature as either mandatory or optional as well as either abstract or concrete.
+Non-leaf features are often marked as abstract, as they do not have to be implemented.
+In addition features can be marked as either mandatory or optional.
 The possible relationships of multiple features with a mutual parent feature are \textit{OR} (at least one feature has to be selected), \textit{ALTERNATIVE} (exactly one feature has to be selected) and \textit{AND} (any number of features can be selected).
 As features' relations may be of higher complexity than just parent-child relations additional constraints can be noted within a feature model.
-Constraints are boolean expressions, the example in figure~\ref{img-fm} shows an implication.
+Constraints can contain any boolean expression.
+
+Figure~\ref{img-fm} shows an example of a simple feature model diagram.
+The node labeled "GraphLibrary" is the root feature and represents the whole Project.
+It contains the nodes "Edges" that has to be selected doe to the mandatory marker and "Algorithms" that is marked optional.
+The implemented Edge types are "Directed" and "Undirected" from which exactly one has to be chosen.
+From the Algorithms at least one has to be chosen.
+The Constraint beneath the figure~\ref{img-fm} implies that if the feature "Cycle" is selected, the Edge type is set to directed.
 

### 2016-03-15 chapters/background.tex
rework with regard to our advisors feedback

@@
 \subsection{Product configuration}
-Through configuration a concrete product can be derived from a product line. Each valid configuration represents a specific \textit{variant} of the possible products.
+The whole product line is represented by it's feature model, which itself is a set of features with specific interrelations.
+The process of configuration of a product line describes the steps to derive a product from the product line.
+To archive this, one has to select a subset of all the possible features within the product line to meet one's requirements.
+But not all subsets of features result in an actual product.
+The interrelations of the features restrict the possible combinations of features resulting in a \textit{valid} configuration.
+If only one of the requirements from the interrelations between the features is not met, no product can be created and the configuration as such is considered \textit{invalid}.
 
@@
 This process requires a lot of domain knowledge on the one hand and detailed information about each single feature on the other.
-With growing numbers of possible features (and thus growing numbers of possible variants) configuration get more and more complex and turns out to be not trivial.
+With growing numbers of possible features (and thus growing numbers of possible products) configuration requires more and more effort.
+The sheer amount of time needed to iterate over all the features grows to be significant.
+But the even greater problem arises from the possible interactions and interrelations of features, which one has to keep track of during configuration.
+The overhead of configuration might even outright negate the benefit gained from using a product line instead of multiple stand-alone products.
 
-One of the purposes of the feature-oriented approach is saving the effort of creating a whole new product and deriving that product from a product line instead.
-The sheer overhead of configuration might even negate that benefit if configuration grows too complex.
+{\color{red}TODO: introduce partial configuration}
 
 \subsection{Constraints, contradictions, SAT-solver}
-As stated above a feature model may contain constraints in the form of boolean expressions.
-Also, the feature-tree can be expressed as a boolean statement.
-The model shown in figure~\ref{img-fm} can be expressed as follows:
+A feature-tree (from a feature model) can be expressed as a boolean statement.
+The mapping between the individual groups (sub-trees) and the corresponding boolean expression is shown in the folloing list:
+
+{\color{red}TODO: Rules for
+\begin{itemize}
+	\item Or
+	\item Alternative
+	\item And
+\end{itemize}
+}
+These particular groups are joined via a boolean \textit{AND}. For the example feature tree shown in figure~\ref{img-fm} the corresponding boolean expression is as follows:
+\begin{equation}
+\begin{split}
+	GraphLibrary\ \wedge\ Edges\\
+	\wedge\ ((Directed\ \wedge \neg Undirected)\\
+	\vee (\neg Directed\ \wedge\ Undirected))
+\end{split}
+\end{equation}\\
+
+As the feature model not only contains the feature tree, but also additional constraints, these constraints have to be considered in the boolean expression representing the complete feature model.
+They can be linked to one another via boolean \textit{AND}s.
+The connection to the previously created boolean expression of the feature tree is also made through a logical \textit{AND}.
+Thus, the complete resulting boolean expression for the feature model shown in figure~\ref{img-fm} is:
 \begin{equation}

### 2016-03-15 chapters/concept.tex
rework with regard to our advisors feedback

@@
 
-Figure~\ref{img-workflow} shows the general process aimed to archive within this work.
-At the beginning there is only a given product line with the modular code artifacts in their specific subdirectories of the project.
+This work was build around the usage for Odoo\footnote{https://www.odoo.com/}, an open-source tool for enterprise-resource-planing written mainly in python\footnote{https://www.python.org/}.
+In this chapter, we will explain the workflow shown in figure~\ref{img-workflow} on the basis of the experiences we made with Odoo.
+
+Odoo itself is programmed as a product line.
+It has a lot of modular code artifacts in their specific subdirectories of the project.
 These code artifacts follow certain conventions to describe their integration in the context of the whole project.
 
-Using these conventions a feature model gets extracted in which the hierarchies and dependencies of the code artifacts are included.
-This allows for much better overview or automated optimization, for example scanning for dead features via SAT-solver.
+Using these conventions we were able to extract a feature model in which the hierarchies and dependencies of the code artifacts are included.
+This allows for much better overview over the product line and it's capabilities.
+During our efforts to implement a automated generation of a feature model we encountered some problems for which we had to find solutions/workarounds.
+
+{\color{red}TODO: State the problems:
+\begin{itemize}
+\item Error-Handling on failure to comply the conventions
+\item Missing Parent Features $\rightarrow$ Abstract features (can be configured beforehand)
+\end{itemize}}
+
 The extracted feature model will also be used in the following step of configuration.
@@
 This domain knowledge is the most challenging part of configurations and restricts most of the possible users to do the configuration on their own.
+The same goes of course for Odoo and the various components contained in the project.
 
-To transfer the domain knowledge of experts to the product line a questionnaire is introduced.
-In the progress of implementing the product line experts also design a questionnaire in such a way that a possible user has to answer a given amount of questions to perform the configuration of a variant meeting his personal needs without him having to know all the details of the implementation of the product line or even the individual features.
-The two major steps of extraction and the creation and usage of the questionnaire are described in detail on the following sections.
+To empower possible users to configure Odoo on their own, we had the idea to use a questionnaire.
+In the progress of implementation, experts also design a questionnaire in such a way that a possible user has to answer a given amount of questions to perform the configuration of a product meeting his personal needs without him having to know all the details of the implementation of the product line or even the individual features.
+This effectively redesigns the process of configuration in such a way, that a user is independent of the knowledge about the details of the implementation and can focus on tailoring the product line to his specific use-case.
+
+The two major steps of extraction of the feature model and the creation and usage of the questionnaire are described in detail on the following sections.
 
@@
 To automatically extract a feature model out of a given software project the structure of that project must be algorithmically processable.
-To archive this, conventions are used for the project of which an overview follows:
+We had a thorough look at the source code of Odoo and found it to be structured according to the following rules:
 
@@
 	\item All features are stored within a specified directory
-	\item Each feature is stored in a separate directory
+	\item Each feature is stored in a separate sub-directory
 	\item A feature's parent features are stated in the name of the corresponding directory
@@
 	\end{itemize}
-	\item Each feature directory contains a configuration file with a specified name containing:
+	\item Each feature directory contains a descriptive file with a specified name containing:
 	\begin{itemize}
@@
 
-All of these information are included in the resulting feature model.
+Following these rules we were able to automatically extract the information needed to generate a feature model.
+For this procedure we implemented a plugin for FeatureIDE which processes the extracted information to a feature model.
+The procedure to generate a feature model is stated following.
+
  The most obvious correspondence lies within the hierarchy.
 The parent names are parsed from the directory name and -if existing- looked up in the existing partial feature model from the previously parsed features.
-As the directories are parsed in alphabetical order a parent feature will always be processed before it's child features.
+As the directories are parsed in alphabetical order and this way of ordering places e.g.
+``Feature1'' in front of ``Feature1\_Feature'', a parent feature will always be processed before it's child features.
 
-After placing it in the correct position within the existing partial feature model each feature's configuration file gets processed.
+After placing it in the correct position within the existing partial feature model each feature's descriptive file gets processed.
 Each feature gets enriched with it's descriptive details and it's dependencies.
@@
 The remaining dependencies are stated as constraints.
-To shorten the list of constraints shared dependencies between multiple features are combined to a single constraint.\\
-
-{\color{red}TODO: State the problems:
-\begin{itemize}
-\item Error-Handling on failure to comply the conventions
-\item Missing Parent Features $\rightarrow$ Abstract features (can be configured beforehand)
-\end{itemize}}
+To shorten the list of constraints shared dependencies between multiple features are combined to a single constraint.
 
@@
 				<label>Answer label</label>
-				<description>Answer description</description>
+				<description>
+					Answer description
+				</description>
 				<dependencies>
-					<feature selection="false">Unselected feature</feature>
+					<feature selection="false">
+						Unselected feature
+					</feature>
 					<feature>selected feature</feature>
@@
 
-\begin{tabular}{ l | l | l }
+\begin{tabulary}{\linewidth}{LLL}
 \textbf{Tag} & \textbf{attributes} & \textbf{child tags}\\
 \hline
-\hline
 configurationSurvey & & projectName, section, page\\
-\hline
 section & id & name, description\\
-\hline
 page & id, sectionId & question, answers\\
-\hline
 answers & type & answer\\
-\hline
 answer & nextPageId & label, description, dependencies\\
-\hline
 dependencies & & feature\\
-\hline
 feature & selection & \\
-\end{tabular}\\
+\end{tabulary}\vspace{2.5em}
 

### 2016-03-22 chapters/background.tex
included the next iteration of feedback

@@
-In the scope of simplifying the configuration of a given product line some specific tools and techniques were used.
-This section will give an overview of what was used in this work to archive the simplification.
+In the scope of supporting the configuration of a given product line some specific tools and techniques are used.
+This sectionl gives an overview of what is used in this work to archive the simplification.
 
@@
 \end{itemize}
-Although feature models can be represented as a boolean formula in CNF or grammer (GUIDSL), it is typically represented in form of a feature diagram and constraints.
-The feature diagram is basically structured as a tree: There is a root node, an arbitrary number of levels of nodes and finally leaf nodes without child nodes of their own.
+Although feature models can be represented as a boolean formula in CNF, it is typically represented in form of a feature diagram.
+The feature diagram is structured as a tree.
 In that manner feature models map the hierarchy of features.
-Non-leaf features are often marked as abstract, as they do not have to be implemented.
-In addition features can be marked as either mandatory or optional.
-The possible relationships of multiple features with a mutual parent feature are \textit{OR} (at least one feature has to be selected), \textit{ALTERNATIVE} (exactly one feature has to be selected) and \textit{AND} (any number of features can be selected).
+The possible relationships of features with a common parent feature are \textit{or}, \textit{alternative} and \textit{and}.
+In the case of an \textit{or}-group, at least one of the child features has to be selected if the parent feature is selected.
+Within an \textit{alternative}-group exactly one of the child feature has to be selected if the parent feature is selected.
+When grouped with an \textit{and}-relation, any number of child features can be selected, if the parent feature is selected.
+In addition, child features in an \textit{and}-group can be marked as either mandatory or optional.
 As features' relations may be of higher complexity than just parent-child relations additional constraints can be noted within a feature model.
-Constraints can contain any boolean expression.
+Constraints can contain any propositional expression.
 
-Figure~\ref{img-fm} shows an example of a simple feature model diagram.
-The node labeled "GraphLibrary" is the root feature and represents the whole Project.
-It contains the nodes "Edges" that has to be selected doe to the mandatory marker and "Algorithms" that is marked optional.
-The implemented Edge types are "Directed" and "Undirected" from which exactly one has to be chosen.
-From the Algorithms at least one has to be chosen.
-The Constraint beneath the figure~\ref{img-fm} implies that if the feature "Cycle" is selected, the Edge type is set to directed.
+Figure~\ref{img-fm} shows an example of a simple feature model.
+The node \textit{GraphLibrary} is the root feature.
+It contains the node \textit{Edges} that has to be selected due to the mandatory marker and \textit{Algorithms} that is marked optional.
+The implemented edge types are \textit{Directed} and \textit{Undirected} from which exactly one has to be chosen as they are mutually exclusive.
+From the algorithms at least one has to be chosen whenever \textit{Algorithms} is selected.
+The constraint beneath Figure~\ref{img-fm} implies that if the feature \textit{Cycle} is selected, the edge type needs to be directed.
 
 \subsection{Product configuration}
-The whole product line is represented by it's feature model, which itself is a set of features with specific interrelations.
+The variability of a product line is represented by it's feature model, which itself is a set of features with specific interrelations.
 The process of configuration of a product line describes the steps to derive a product from the product line.
-To archive this, one has to select a subset of all the possible features within the product line to meet one's requirements.
-But not all subsets of features result in an actual product.
+To archive this, a user has to select a subset of all the possible features within the product line to meet his requirements.
+However, not all subsets of features result in a valid product.
 The interrelations of the features restrict the possible combinations of features resulting in a \textit{valid} configuration.
@@
 During configuration a user selects or unselects features to his needs.
-This process requires a lot of domain knowledge on the one hand and detailed information about each single feature on the other.
-With growing numbers of possible features (and thus growing numbers of possible products) configuration requires more and more effort.
-The sheer amount of time needed to iterate over all the features grows to be significant.
-But the even greater problem arises from the possible interactions and interrelations of features, which one has to keep track of during configuration.
+This process requires a lot of domain knowledge on the one hand and detailed information about the implementation of each single feature on the other.
+With growing numbers of features and thus growing numbers of possible products configuration requires more effort.
+However, the even greater problem arises from the possible interactions and interrelations of features, which one has to keep track of during configuration.
 The overhead of configuration might even outright negate the benefit gained from using a product line instead of multiple stand-alone products.
+This trade-off has to be considered or addressed through modification of the configuration process.
 
@@
 
-\subsection{Constraints, contradictions, SAT-solver}
-A feature-tree (from a feature model) can be expressed as a boolean statement.
-The mapping between the individual groups (sub-trees) and the corresponding boolean expression is shown in the folloing list:
+\subsection{Satisfiability}
+A feature model can be expressed as a propositional statement. The mapping between the individual groups (sub-trees) and the corresponding propositional expression is shown in the following list:
 
@@
 }
-These particular groups are joined via a boolean \textit{AND}. For the example feature tree shown in figure~\ref{img-fm} the corresponding boolean expression is as follows:
+These particular groups are joined via a logical \textit{AND}. For the example feature model shown in Figure~\ref{img-fm} the corresponding propositional expression is as follows:
 \begin{equation}
@@
 As the feature model not only contains the feature tree, but also additional constraints, these constraints have to be considered in the boolean expression representing the complete feature model.
-They can be linked to one another via boolean \textit{AND}s.
-The connection to the previously created boolean expression of the feature tree is also made through a logical \textit{AND}.
-Thus, the complete resulting boolean expression for the feature model shown in figure~\ref{img-fm} is:
+They can be linked to one another via logical \textit{AND}s.
+The connection to the previously created propositional expression of the feature tree is also made through a logical \textit{AND}.
+Thus, the complete resulting propositional expression for the feature model shown in Figure~\ref{img-fm} is:
 \begin{equation}
@@
 This formalism allows a configuration to be checked for validity.
-To do so each selected Feature is appended with a logical \textit{AND} and each specifically unselected feature is also appended with a logical \textit{AND} but gets negated.
+To do so each selected feature is appended with a logical \textit{AND} and each specifically unselected feature is also appended with a logical \textit{AND} but gets negated.
 The resulting expression is then evaluated by a SAT-solver to check for satisfiability.

### 2016-03-22 chapters/concept.tex
included the next iteration of feedback

@@
 Using these conventions we were able to extract a feature model in which the hierarchies and dependencies of the code artifacts are included.
-This allows for much better overview over the product line and it's capabilities.
-During our efforts to implement a automated generation of a feature model we encountered some problems for which we had to find solutions/workarounds.
+This allows for overview over the product line and it's variability.
+During our efforts to implement an automated generation of a feature model we encountered some problems for which we had to find solutions/workarounds.
 
@@
 
-The extracted feature model will also be used in the following step of configuration.
+The extracted feature model is also used in the following step of configuration. There, it visualizes the interrelations of the features and supports the understanding of the configuration steps.
 
-Configuration of product lines generally requires a good understanding of the given problems and the possible solutions to these problems as well as the specific implementations of these solutions.
+Configuration of product lines requires a good understanding of the given problems and the possible solutions to these problems as well as the specific implementations of these solutions.
 This domain knowledge is the most challenging part of configurations and restricts most of the possible users to do the configuration on their own.
@@
 
-To empower possible users to configure Odoo on their own, we had the idea to use a questionnaire.
+To empower possible users to configure \textit{Odoo} on their own, our approach is to use a questionnaire.
 In the progress of implementation, experts also design a questionnaire in such a way that a possible user has to answer a given amount of questions to perform the configuration of a product meeting his personal needs without him having to know all the details of the implementation of the product line or even the individual features.
@@
 To automatically extract a feature model out of a given software project the structure of that project must be algorithmically processable.
-We had a thorough look at the source code of Odoo and found it to be structured according to the following rules:
+We had a thorough look at the source code of \textit{Odoo} and found it to be structured according to the following rules:
 
@@
 
-Following these rules we were able to automatically extract the information needed to generate a feature model.
+Following these rules we automatically extract the information needed to generate a feature model.
 For this procedure we implemented a plugin for FeatureIDE which processes the extracted information to a feature model.
@@
 
- The most obvious correspondence lies within the hierarchy.
+The strongest correspondence lies within the hierarchy.
 The parent names are parsed from the directory name and -if existing- looked up in the existing partial feature model from the previously parsed features.
@@
 
+We applied these steps to a total of A files, thus extracting B features for \textit{Odoo}.
+These features are arranged in a total of C hierarchical levels.
+Additionally, D constraints limit the possible valid configurations.
+
 \subsection{Questionnaire Approach}
-As stated above configuration is one of the most challenging tasks within the scope of software product lines.
-In the previous section the automatic extraction of a feature model out of existing source code was explained.
-The resulting feature model yields a much better overview over the possible features and their interrelationships.
-Although the formalism of a feature model allows for tool support to simplify the process of configuration, still a lot of domain knowledge is required to be able to find the right combination of features for a given use-case.
+Configuration is a challenging tasks within the scope of software product lines.
+The resulting feature model from the automated generation yields a better overview over the possible features and their interrelationships.
+Although the formalism of a feature model allows for tool support the process of configuration, still domain knowledge is required to be able to find the right combination of features for a given use-case.
 
-This work therefore introduces a method to allow experts to apply their knowledge and understanding to a whole product line during the development and thus enabling end users to draw on this knowledge whenever a configuration is taking place.
+This work therefore introduces a method to allow experts to apply their knowledge and understanding to a whole product line during the development.
+Thus end users are enabled to draw on this knowledge whenever a configuration is taking place.
 
-In this work we made the decision to use a questionnaire based approach.
+In this work, we made the decision to use a questionnaire-based approach.
 Depending on the implementation of the questionnaire during development a partial or event complete configuration can be archived by a user through just answering the questions of the questionnaire.
-The concrete selection of features gets lifted to a higher level of abstraction.
+The selection of features gets lifted to a higher level of abstraction.
 The user only has to decide between the possible answers presented to him in the questionnaire to best fit to his use-case.
@@
 
-In this work we also introduce a data structure to hold the definition of a questionnaire.
+We also introduce a data structure to hold the definition of a questionnaire.
 To archive easy integration we decided for a definition in XML.
@@
 </configurationSurvey>
+\caption{Examplary XML file for a  questionnaire}
 \end{lstlisting}

### 2016-03-22 chapters/intro.tex
included the next iteration of feedback

--- 2016-03-10 chapters/intro.tex
@@
 % and "HIS" in caps to complete the first word.
-\IEEEPARstart{D}{eveloping} software product lines can result in a great amount of variants, when customizing the Software to each customers needs.
+Developing software product lines can result in a large amount of variants, when customizing the software to each customers needs.
 By developing with a feature-oriented approach the configuration of a single variant can be done by selecting the features a customer needs, automatically including its dependencies.
@@
 Feature Models are essential structures for the feature-oriented development and later configuration of software product lines (SPL).
-In such a way that they give a complete and easily understandable overview of the given features and constraints of a product-line.
-There are projects being developed feature-oriented, but don't have a feature model yet.
+They give a complete and understandable overview of the given features and constraints of a product-line.
+There are projects being developed in a feature-oriented manner, but don't have a feature model yet.
+Implementing it on top of a given Project can result in a complex task due to the amount of its features and the constraints between them.
+Additionally, those information are often already kept inside of readme or configuration files, what predesignates them to be analyzed programmatically.
 This work aims at automatically generating it out of descriptive files and naming conventions, to simplify a big part of the feature model creation.
 
-Although the feature configuration gives  Developers the ability to create custom variants, there still has to be a consultant explaining the features to the customer, trying to figure out his current and future needs.
-As the Software grows and gets more features, this process gets more difficult, as you can no longer explain all the features, but you still have to figure out if the customer needs them or not.
-
+Although the feature configuration gives developers the ability to create custom variants, there still has to be a consultant explaining the features to the customer, trying to figure out his current and future needs.
+As the software grows and gets more features, this process gets difficult, as one can no longer explain all the features, but you still have to figure out if the customer needs them or not.
 This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
 
-\section*{Problem statement}
-Very high complexity of configuration due to many features and constraints.
-Domain knowledge is highly required to understand the given software product-line and being able to combine it's features to a valid configuration which satisfies the users needs.
+FeatureIDE is an open source IDE for feature-oriented-software development.
+It provides all the functionality needed to programatically generate and work with Feature Models.
+The underlying Eclipse enables us to implement the feature extraction and the questionnaire as a plugin.
 
-\section*{Contribution}
+This work demonstratea the named simplifications based on a real life Project.
+This software, an open source ERP System called \textit{Odoo}\footnote{https://www.odoo.com/} is predestined to be developed feature-oriented due to a huge amount of features and complex constraints.
+The Project is currently being developed and structured feature oriented, although it doest't contain a Feature Model yet.
+Furthermore, \textit{Odoo} reached a critical amount of features where a salesman cannot consult a customer by going through all of the features anymore, but has to come up with a more effective way.
 
-Simplifying the process of configuration of product lines through extracting a feature model out of naming conventions and configuration files from an existing product line in FeatureIDE and applying a configuration wizard which guides the user though the creation of a specific product (variant) in the style of a questionnaire, thus applying the domain knowledge of an expert.
-
-%This\cite{fpe} is\cite{qdc} a\cite{qbvm} dummy\cite{fmgp} to create citations.
+Contributions:
+\begin{itemize}
+\item foo
+\item bar
+\item baz
+\end{itemize}

### 2016-03-23 chapters/intro.tex
Introduction fix

@@
 % and "HIS" in caps to complete the first word.
+Developing feature oriented, although bringing with it some overhead, facilitates the creation of software when it is planned on custom tailoring it for a multiple number of clients.
+Feature oriented means developing and maintaining single features that can be combined with others to create a whole product.
+All of the individual features make up a product line, whereas a subset of those features create a variant of this product.
 Developing software product lines can result in a large amount of variants, when customizing the software to each customers needs.
@@
 
+% TODO: fosd buch zitieren, FM Zitat
 Feature Models are essential structures for the feature-oriented development and later configuration of software product lines (SPL).
@@
 Implementing it on top of a given Project can result in a complex task due to the amount of its features and the constraints between them.
-Additionally, those information are often already kept inside of readme or configuration files, what predesignates them to be analyzed programmatically.
+Nevertheless the benefits of a correct feature model justify the effort to extract one out of a live project.
 This work aims at automatically generating it out of descriptive files and naming conventions, to simplify a big part of the feature model creation.
@@
 
-FeatureIDE is an open source IDE for feature-oriented-software development.
-It provides all the functionality needed to programatically generate and work with Feature Models.
+FeatureIDE is an open source IDE for feature-oriented-software development. It provides all the functionality needed to programmatically generate and work with feature models.
+% TODO: was benutzt ihr denn genau?
  The underlying Eclipse enables us to implement the feature extraction and the questionnaire as a plugin.
 
-This work demonstratea the named simplifications based on a real life Project.
-This software, an open source ERP System called \textit{Odoo}\footnote{https://www.odoo.com/} is predestined to be developed feature-oriented due to a huge amount of features and complex constraints.
-The Project is currently being developed and structured feature oriented, although it doest't contain a Feature Model yet.
+This work demonstrates the feature model extraction and questionnaire creation based on a real life Project.
+The Project, an open source ERP system called \textit{Odoo}\footnote{https://www.odoo.com/} is predestined to be developed feature-oriented due to a huge amount of features and complex constraints.
+It is currently being developed and structured feature oriented, although it doest't contain a feature model yet.
 Furthermore, \textit{Odoo} reached a critical amount of features where a salesman cannot consult a customer by going through all of the features anymore, but has to come up with a more effective way.
@@
 \begin{itemize}
-\item foo
-\item bar
-\item baz
+\item Automatic feature model generation based on descriptive files and naming conventions
+\item Eclipse plugin, that enables the creation of a questionnaire based on a configuration file and the associated feature model
+\item The questionnaire changes as choices are made based on the logic behind the configuration file and the dependencies of the feature model
+\item Exiting the questionnaire always results in a valid configured variant 
 \end{itemize}

### 2016-03-23 chapters/background.tex
Changed image to vector image, minor text corrections in chapter 2a

@@
 In the scope of supporting the configuration of a given product line some specific tools and techniques are used.
-This sectionl gives an overview of what is used in this work to archive the simplification.
+This section gives an overview of what is used in this work to archive the simplification.
 
@@
 \begin{figure}
-	\includegraphics{img/img-fm.png}
+	\includegraphics{img/img-fm.pdf}
 	\caption{A simple example of a feature model}
@@
 \end{figure}
-Amongst their benefits are:
-\begin{itemize}
-\item Can be visualized as a feature diagram, showing the possible features and their hierarchy
-\item Classification of features and their dependencies (alternative/or; optional/mandatory/abstract)
-\item Formal Representation of the whole product line as a feature diagram $\Rightarrow$ computationally processable
-\item Enables configuration and variant validation
-\end{itemize}
+One of their benefits is the visualization as a feature diagram, providing an overview of the containing features, and their hierarchy and dependencies.
+In addition it classifies the features and their dependencies by Ordinality (Optional/mandatory), logical operator (Disjunction/exclusive disjunction) and whether it is abstract or concrete.
+Furthermore it contains all information needed to provide a configuration of Features and its validation.
+
 Although feature models can be represented as a boolean formula in CNF, it is typically represented in form of a feature diagram.
@@
 The node \textit{GraphLibrary} is the root feature.
-It contains the node \textit{Edges} that has to be selected due to the mandatory marker and \textit{Algorithms} that is marked optional.
+Its descendants are the node \textit{Edges}, that has to be selected due to the mandatory marker, and \textit{Algorithms} that is marked optional.
 The implemented edge types are \textit{Directed} and \textit{Undirected} from which exactly one has to be chosen as they are mutually exclusive.
@@
 
-During configuration a user selects or unselects features to his needs.
+During configuration a user selects or deselects features to his needs.
 This process requires a lot of domain knowledge on the one hand and detailed information about the implementation of each single feature on the other.

### 2016-03-26 chapters/concept.tex
TODOs added
workflow chapter is now more abstract

@@
 
+%TODO: Abstrakte Beschreibung des Nutzer-Szenarios
+
+%TODO: Schaubild
 unstructured product line $\rightarrow$ generated feature model $\rightarrow$ optimizing (via SAT-solver?) $\rightarrow$ domain knowledge of an expert $\Rightarrow$ Questionnaire $\rightarrow$ Feature model + Questionnaire $\Rightarrow$ Product (variant)\\
 
-This work was build around the usage for Odoo\footnote{https://www.odoo.com/}, an open-source tool for enterprise-resource-planing written mainly in python\footnote{https://www.python.org/}.
-In this chapter, we will explain the workflow shown in figure~\ref{img-workflow} on the basis of the experiences we made with Odoo.
+This chapter describes the general workflow we aim to archive within this work.
+This workflow can be seen in Figure~\ref{img-workflow}.
+To start off, some kind of software product line is required.
+It's source code has to be structured in a way that allows for an algorithm to recognize the individual features as well as their interrelations, especially the hierarchical dependencies.
 
-Odoo itself is programmed as a product line.
-It has a lot of modular code artifacts in their specific subdirectories of the project.
-These code artifacts follow certain conventions to describe their integration in the context of the whole project.
+The two major steps of extraction of the feature model and the creation and usage of the questionnaire are described in detail in the following sections.
 
-Using these conventions we were able to extract a feature model in which the hierarchies and dependencies of the code artifacts are included.
+\subsection{Extraction of a Feature Model}
+Out of the given structure we extract the hierarchies of the features as well as additional dependencies.
+These are the input for the automated generation of a feature model.
 This allows for overview over the product line and it's variability.
-During our efforts to implement an automated generation of a feature model we encountered some problems for which we had to find solutions/workarounds.
+During our efforts to implement an automated generation of a feature model we encounter some problems for which we have to find solutions/workarounds.
 
-{\color{red}TODO: State the problems:
-\begin{itemize}
-\item Error-Handling on failure to comply the conventions
-\item Missing Parent Features $\rightarrow$ Abstract features (can be configured beforehand)
-\end{itemize}}
+The first problem consists of finding the structures of the given source code and processing them algorithmically.
+Most software complies to conventions regarding the naming and structuring of directories.
+We try to make use of these conventions.
+But as they are just conventions and not rules, in most source code one will find violations of the conventions.
+Instead of interrupting the whole process, we implement error handling.
+The result is a notification for the user to alert the developers about the error.
+Also, the remaining information, which aren't immediately affected by the error, are still extracted and used for the generation of the feature model, if possible.
+
+Another challenge lies within the order of processing the features during the creation of the feature model.
+To correctly reproduce the hierarchy of the features, features have to be declared as child features of their parents.
+If the declared parent feature doesn't already exist, the creation of a feature model fails.
+So we have to ensure for each feature, that it gets processed after it's parent feature.
+
+Another error we found is one ore more features having a parent feature which doesn't exist as a code artifact itself.
+Thus, the parent feature doesn't exists in the feature model and it's child features can't be placed in the hierarchy in the correct place.
+To still include these features in the feature model we create an abstract feature for the parent feature.
+The abstract feature is a direct child of the root feature.
+But as it doesn't have any describing code, it only has a name and no additional descriptive details.
 
 The extracted feature model is also used in the following step of configuration. There, it visualizes the interrelations of the features and supports the understanding of the configuration steps.
-
-Configuration of product lines requires a good understanding of the given problems and the possible solutions to these problems as well as the specific implementations of these solutions.
-This domain knowledge is the most challenging part of configurations and restricts most of the possible users to do the configuration on their own.
-The same goes of course for Odoo and the various components contained in the project.
-
-To empower possible users to configure \textit{Odoo} on their own, our approach is to use a questionnaire.
-In the progress of implementation, experts also design a questionnaire in such a way that a possible user has to answer a given amount of questions to perform the configuration of a product meeting his personal needs without him having to know all the details of the implementation of the product line or even the individual features.
-This effectively redesigns the process of configuration in such a way, that a user is independent of the knowledge about the details of the implementation and can focus on tailoring the product line to his specific use-case.
-
-The two major steps of extraction of the feature model and the creation and usage of the questionnaire are described in detail on the following sections.
-
-\subsection{Extraction of a feature model}
-To automatically extract a feature model out of a given software project the structure of that project must be algorithmically processable.
-We had a thorough look at the source code of \textit{Odoo} and found it to be structured according to the following rules:
-
-\begin{itemize}
-	\item All features are stored within a specified directory
-	\item Each feature is stored in a separate sub-directory
-	\item A feature's parent features are stated in the name of the corresponding directory
-	\begin{itemize}
-		\item The complete hierarchy is displayed, except for the root feature
-		\item Individual parent features are delimited with an unique symbol
-	\end{itemize}
-	\item Each feature directory contains a descriptive file with a specified name containing:
-	\begin{itemize}
-		\item A descriptive name of the feature
-		\item A description text for the feature
-		\item All dependencies including the parent features
-	\end{itemize}
-\end{itemize}
-
-Following these rules we automatically extract the information needed to generate a feature model.
-For this procedure we implemented a plugin for FeatureIDE which processes the extracted information to a feature model.
-The procedure to generate a feature model is stated following.
-
-The strongest correspondence lies within the hierarchy.
-The parent names are parsed from the directory name and -if existing- looked up in the existing partial feature model from the previously parsed features.
-As the directories are parsed in alphabetical order and this way of ordering places e.g.
-``Feature1'' in front of ``Feature1\_Feature'', a parent feature will always be processed before it's child features.
-
-After placing it in the correct position within the existing partial feature model each feature's descriptive file gets processed.
-Each feature gets enriched with it's descriptive details and it's dependencies.
-The list of dependencies firstly gets reduced by the parent features as the feature models hierarchy already implements this kind of dependencies.
-The remaining dependencies are stated as constraints.
-To shorten the list of constraints shared dependencies between multiple features are combined to a single constraint.
-
-We applied these steps to a total of A files, thus extracting B features for \textit{Odoo}.
-These features are arranged in a total of C hierarchical levels.
-Additionally, D constraints limit the possible valid configurations.
 
@@
 The resulting feature model from the automated generation yields a better overview over the possible features and their interrelationships.
-Although the formalism of a feature model allows for tool support the process of configuration, still domain knowledge is required to be able to find the right combination of features for a given use-case.
+Although the formalism of a feature model allows for tool support for the process of configuration, still domain knowledge is required to be able to find the right combination of features for a given use-case.
 
 This work therefore introduces a method to allow experts to apply their knowledge and understanding to a whole product line during the development.
-Thus end users are enabled to draw on this knowledge whenever a configuration is taking place.
+Thus, users are enabled to draw on this knowledge whenever a configuration is taking place.
 
 In this work, we made the decision to use a questionnaire-based approach.
-Depending on the implementation of the questionnaire during development a partial or event complete configuration can be archived by a user through just answering the questions of the questionnaire.
+In the progress of implementation, experts also design a questionnaire.
+They do so in such a way, that a user has to answer a given amount of questions to perform the configuration of a product.
+Depending on the implementation of the questionnaire, a partial or even complete configuration can be archived by a user through just answering the questions of the questionnaire.
+
 The selection of features gets lifted to a higher level of abstraction.
@@
 Internally the selected answers are mapped to a specified (un-)selection of features so the user avoids the hassle of considering implementation-details of each feature.
+This effectively redesigns the process of configuration in such a way, that a user is independent of the knowledge about the details of the implementation and can focus on tailoring the product line to his specific use-case.
 
@@
 It always contains at least a Question and more then one possible answer.
-The answers can be grouped analogous to the grouping of features in a feature model: \textit{OR} (at least one answer has to be selected), \textit{ALTERNATIVE} (exactly one answer has to be selected) and \textit{AND} (any number of answers can be selected).
+The answers can be grouped analogous to the grouping of features in a feature model: \textit{or} (at least one answer has to be selected), \textit{alternative} (exactly one answer has to be selected) and \textit{and} (any number of answers can be selected).
 
@@
 
+\begin{figure}
 \begin{lstlisting}
@@
 </configurationSurvey>
+\end{lstlisting}
 \caption{Examplary XML file for a  questionnaire}
-\end{lstlisting}
+\end{figure}
 
@@
 \begin{itemize}
-\item configurationSurvey: The root tag to contain all other tags for the questionnaire.
-\item section: Enables grouping of question-pages. Also displays the name and description at the top of every page.
-\item page: Contains a question and the corresponding answers. Also has an indicator for a section
-\item answers: Contains the individual possible answers and groups them in the specified manner.
-\item answer: Defines the displayed text of an answer as well as the corresponding features. Can also have an indicator for the next page.
-\item dependencies: Defines the (un-)selection of features, if the corresponding answer gets selected.
+\item \texttt{configurationSurvey}: The root tag to contain all other tags for the questionnaire.
+\item \texttt{section}: Enables grouping of question-pages. Also displays the name and description at the top of every page.
+\item \texttt{page}: Contains a question and the corresponding answers. Also has an indicator for a section
+\item \texttt{answers}: Contains the individual possible answers and groups them in the specified manner.
+\item \texttt{answer}: Defines the displayed text of an answer as well as the corresponding features. Can also have an indicator for the next page.
+\item \texttt{dependencies}: Defines the (un-)selection of features, if the corresponding answer gets selected.
 \end{itemize}
+
+%TODO: Am ende kommt ein konfiguriertes Produkt raus.

### 2016-03-26 chapters/scenarios.tex
slight restructuring
short notes for each section
TODOs added
workflow chapter is now more abstract

@@
-State a few usage scenarios and show why the questionnaire is better or as good as the existing solutions. Also point out in which scenario this might be the wrong tool.
+State the process of FM-Extraction on the example of \textit{Odoo}.
+
+We applied these steps to a total of [A] files, thus extracting [B] features for \textit{Odoo}.
+These features are arranged in a total of [C] hierarchical levels.
+Additionally, [D] constraints limit the possible valid configurations of \textit{Odoo}.
+
+Also state how some of the questions and their mapping in the questionnaire were developed.
+
+Finally, show the process of configuration through running a fictinal user over the questionnaire and document his decisions as well as the resulting configurations.
+
+%TODO: test ausdenken, der alle ``Fähgkeiten'' zeigt
+
+% Fahrradladen, Online-Shop, Social-Media, Bezahldienste, Kontakt-Portal, DE/EN, Newsletter
+%
+% Website builder, eCommerce, SEA
+% Sales, CRM, invoicing, Point of Sale
+% Inventory, Purchase
+% Email Marketing, Survey
+
+%TODO: Planung, durchführung, Auswertung
+
+%TODO: nur ein konstruierter Fall, weil Domain Knowledge fehlt.

### 2016-03-27 chapters/background.tex
TODOs added
contributions fixed, workflow image added, citation added

@@
 However, the even greater problem arises from the possible interactions and interrelations of features, which one has to keep track of during configuration.
-The overhead of configuration might even outright negate the benefit gained from using a product line instead of multiple stand-alone products.
-This trade-off has to be considered or addressed through modification of the configuration process.
+The automatic selection or deselection of a features doe to propagation of a made selection always results in a valid configuration.
+Nevertheless the propagated selections can be confusing for the user.
 
-{\color{red}TODO: introduce partial configuration}
+A non-final configuration, that is a configuration that still has some feature choices left to be made, is called a \textit{partial configuration}.
+A \textit{valid} partial configuration can be useful, as it narrows down the number of possible resulting variations and choices left to make.
 
 \subsection{Satisfiability}
+%TODO: rausschmeißen?
 A feature model can be expressed as a propositional statement. The mapping between the individual groups (sub-trees) and the corresponding propositional expression is shown in the following list:

### 2016-03-27 chapters/intro.tex
TODOs added
contributions fixed, workflow image added, citation added

@@
 The configuration is based on a Feature Model, that defines the available Features and its relations to one another.
+A feature model documents the features of a product line and their relationships\cite{fospl}.
 
-% TODO: fosd buch zitieren, FM Zitat
 Feature Models are essential structures for the feature-oriented development and later configuration of software product lines (SPL).
-They give a complete and understandable overview of the given features and constraints of a product-line.
 There are projects being developed in a feature-oriented manner, but don't have a feature model yet.
@@
 
-FeatureIDE is an open source IDE for feature-oriented-software development. It provides all the functionality needed to programmatically generate and work with feature models.
-% TODO: was benutzt ihr denn genau?
+FeatureIDE is an open source IDE for feature-oriented-software development.
+It provides all the functionality needed to programmatically generate and work with feature models.
+This includes the logic behind configurations, data structures and the visualization and processing of feature models.
 The underlying Eclipse enables us to implement the feature extraction and the questionnaire as a plugin.
@@
 \begin{itemize}
-\item Automatic feature model generation based on descriptive files and naming conventions
-\item Eclipse plugin, that enables the creation of a questionnaire based on a configuration file and the associated feature model
-\item The questionnaire changes as choices are made based on the logic behind the configuration file and the dependencies of the feature model
-\item Exiting the questionnaire always results in a valid configured variant 
+\item Automatic feature model generation based on descriptive files and naming conventions as a foundation for the thereon based questionnaire.
+\item Eclipse plugin, that enables the creation of a questionnaire based on a configuration file and the associated feature model.
+The liberties of the configuration file specification allows very personalized questionnaires.
+\item The questionnaire changes as choices are made based on the logic behind the configuration file and the dependencies of the feature model.
+This enables a responsive questionnaire that prevents unnecessary questions.
+\item Exiting the questionnaire always results in a valid configured variant to always ensure a valid configuration.
 \end{itemize}

### 2016-03-27 chapters/concept.tex
contributions fixed, workflow image added, citation added
xml coloring added
minor visual changes

@@
-[Diagram showing the general workflow]
-
-%TODO: Abstrakte Beschreibung des Nutzer-Szenarios
-
-%TODO: Schaubild
-unstructured product line $\rightarrow$ generated feature model $\rightarrow$ optimizing (via SAT-solver?) $\rightarrow$ domain knowledge of an expert $\Rightarrow$ Questionnaire $\rightarrow$ Feature model + Questionnaire $\Rightarrow$ Product (variant)\\
+%unstructured product line $\rightarrow$ generated feature model $\rightarrow$ %optimizing (via SAT-solver?) $\rightarrow$ domain knowledge of an expert %$\Rightarrow$ Questionnaire $\rightarrow$ Feature model + Questionnaire %$\Rightarrow$ Product (variant)\\
 
@@
 It's source code has to be structured in a way that allows for an algorithm to recognize the individual features as well as their interrelations, especially the hierarchical dependencies.
+
+\begin{figure}[H]
+	\includegraphics{img/img-workflow.pdf}
+	\caption{Diagram showing the general workflow}
+	\label{img-workflow}
+\end{figure}
 
@@
 To archive easy integration we decided for a definition in XML.
-We defined the necessary tags to create a questionnaire which are displayed in the following code snippet:
+We defined the necessary tags to create a questionnaire which are displayed in figure~\ref{fig:xmlFigure}.
 
-\begin{figure}
+\begin{figure}[H]
+\begin{tabulary}{\linewidth}{LLL}
+\textbf{Tag} & \textbf{attributes} & \textbf{child tags}\\
+\hline
+configurationSurvey & & projectName, section, page\\
+section & id & name, description\\
+page & id, sectionId & question, answers\\
+answers & type & answer\\
+answer & nextPageId & label, description, dependencies\\
+dependencies & & feature\\
+feature & selection & \\
+\end{tabulary}\vspace{2.5em}
+\end{figure}
+
+The individual tags are explained as follows:
+\begin{itemize}
+\item \texttt{configurationSurvey}: The root tag to contain all other tags for the questionnaire.
+\item \texttt{section}: Enables grouping of question-pages. Also displays the name and description at the top of every page.
+\item \texttt{page}: Contains a question and the corresponding answers. Also has an indicator for a section
+\item \texttt{answers}: Contains the individual possible answers and groups them in the specified manner.
+\item \texttt{answer}: Defines the displayed text of an answer as well as the corresponding features. Can also have an indicator for the next page.
+\item \texttt{dependencies}: Defines the (un-)selection of features, if the corresponding answer gets selected.
+\end{itemize}
+
+\begin{figure}[H]
+	\lstset{language=XML}
 	\begin{lstlisting}
@@
 	\caption{Examplary XML file for a  questionnaire}
+	\label{fig:xmlFigure}
 \end{figure}
 
-\begin{tabulary}{\linewidth}{LLL}
-\textbf{Tag} & \textbf{attributes} & \textbf{child tags}\\
-\hline
-configurationSurvey & & projectName, section, page\\
-section & id & name, description\\
-page & id, sectionId & question, answers\\
-answers & type & answer\\
-answer & nextPageId & label, description, dependencies\\
-dependencies & & feature\\
-feature & selection & \\
-\end{tabulary}\vspace{2.5em}
-
-The individual tags are explained as follows:
-
-\begin{itemize}
-\item \texttt{configurationSurvey}: The root tag to contain all other tags for the questionnaire.
-\item \texttt{section}: Enables grouping of question-pages. Also displays the name and description at the top of every page.
-\item \texttt{page}: Contains a question and the corresponding answers. Also has an indicator for a section
-\item \texttt{answers}: Contains the individual possible answers and groups them in the specified manner.
-\item \texttt{answer}: Defines the displayed text of an answer as well as the corresponding features. Can also have an indicator for the next page.
-\item \texttt{dependencies}: Defines the (un-)selection of features, if the corresponding answer gets selected.
-\end{itemize}
-
 %TODO: Am ende kommt ein konfiguriertes Produkt raus.

### 2016-03-28 chapters/background.tex
Scenario part 1/2 and small grammar fixes

@@
 One of their benefits is the visualization as a feature diagram, providing an overview of the containing features, and their hierarchy and dependencies.
-In addition it classifies the features and their dependencies by Ordinality (Optional/mandatory), logical operator (Disjunction/exclusive disjunction) and whether it is abstract or concrete.
-Furthermore it contains all information needed to provide a configuration of Features and its validation.
+In addition, it classifies the features and their dependencies by Ordinality (Optional/mandatory), logical operator (Disjunction/exclusive disjunction) and whether it is abstract or concrete.
+Furthermore, it contains all information needed to provide a configuration of Features and its validation.
 
@@
 \subsection{Product configuration}
-The variability of a product line is represented by it's feature model, which itself is a set of features with specific interrelations.
+The variability of a product line is represented by its feature model, which itself is a set of features with specific interrelations.
 The process of configuration of a product line describes the steps to derive a product from the product line.
@@
 The automatic selection or deselection of a features doe to propagation of a made selection always results in a valid configuration.
-Nevertheless the propagated selections can be confusing for the user.
+Nevertheless, the propagated selections can be confusing for the user.
 

### 2016-03-28 chapters/intro.tex
Scenario part 1/2 and small grammar fixes

@@
 Feature oriented means developing and maintaining single features that can be combined with others to create a whole product.
-All of the individual features make up a product line, whereas a subset of those features create a variant of this product.
+All the individual features make up a product line, whereas a subset of those features create a variant of this product.
 Developing software product lines can result in a large amount of variants, when customizing the software to each customers needs.
@@
 Implementing it on top of a given Project can result in a complex task due to the amount of its features and the constraints between them.
-Nevertheless the benefits of a correct feature model justify the effort to extract one out of a live project.
+Nevertheless, the benefits of a correct feature model justify the effort to extract one out of a live project.
 This work aims at automatically generating it out of descriptive files and naming conventions, to simplify a big part of the feature model creation.
@@
 The Project, an open source ERP system called \textit{Odoo}\footnote{https://www.odoo.com/} is predestined to be developed feature-oriented due to a huge amount of features and complex constraints.
-It is currently being developed and structured feature oriented, although it doest't contain a feature model yet.
-Furthermore, \textit{Odoo} reached a critical amount of features where a salesman cannot consult a customer by going through all of the features anymore, but has to come up with a more effective way.
+It is currently being developed and structured feature oriented, although it doesn't contain a feature model yet.
+Furthermore, \textit{Odoo} reached a critical amount of features where a salesman cannot consult a customer by going through all the features anymore, but has to come up with a more effective way.
 

### 2016-03-28 chapters/scenarios.tex
Scenario part 1/2 and small grammar fixes

@@
-State the process of FM-Extraction on the example of \textit{Odoo}.
+In the fallowing chapter the workflow described in Chapter~\ref{ch:workflow} is carried out based on the current project status of \textit{Odoo}.
+At first a feature model is generated based on the naming conventions of the project folders and the configuration files contained therein.
+Afterwards the feature model is corrected from any errors that occurred during the generation process.
+The resulting model combined with domain knowledge allows for the creation of a questionnaire that takes a minimum of choices to configure a custom tailored application.
 
-We applied these steps to a total of [A] files, thus extracting [B] features for \textit{Odoo}.
-These features are arranged in a total of [C] hierarchical levels.
+All the Odoo features lie inside of a folder named "addons".
+The code of each feature is contained in its own folder which is named like the parent feature with a suffix of its own name.
+According to this naming convention the feature "website\textunderscore sale" is a child of the feature "website", and parent to "website\textunderscore sale\textunderscore stock".
+In addition to the naming convention, there is a configuration file, written in python in each of the feature folders.
+These files contain a description of the feature, a name, that doesn't always match with the folder name and the dependencies that are required for this feature to work.
+By first creating a list of all features based on the folder names, one can match them to the names inside of the configuration files.
+At this point we realize, that there are some conflicts in the naming of the 261 features.
+For example the feature "sale" is a standalone feature and has nothing to do with the sale from the feature "event\textunderscore sale".
+As the default FeatureIDE doesn't support multiple features with the same name, we decided to leave the full names with the underscores.
+In addition, there are some folder names where the underscore doesn't separate features, like "point\textunderscore of\textunderscore sale".
+For those we implemented naming exceptions where the user can add strings that represent a single feature.
+
+We applied these steps to a total of 261 folders, containing in total more than 18.800 files, extracting 306 features.
+The surplus features result from abstract features, that do not have their own folder, but are implizit in the naming.
+The resulting feature model is arranged in a total of six hierarchical levels.
 Additionally, [D] constraints limit the possible valid configurations of \textit{Odoo}.
+
+%TODO: Auswertung
+TODO:
 

### 2016-03-28 chapters/background.tex
better integration of the satisfiability section

@@
 In the scope of supporting the configuration of a given product line some specific tools and techniques are used.
-This section gives an overview of what is used in this work to archive the simplification.
+This section gives an overview of what is used in this work to archive a simplification of the workflow from a "product line"-like source code base to a final product.
 
-\subsection{Feature Models}
+\subsection{Feature Models} \label{ch:fm}
 Feature models are multi-purpose structure for product lines. 
@@
 
-Although feature models can be represented as a boolean formula in CNF, it is typically represented in form of a feature diagram.
+Although feature models can be represented as a propositional expression in CNF, it is typically represented in form of a feature diagram.
 The feature diagram is structured as a tree.
@@
 The node \textit{GraphLibrary} is the root feature.
-Its descendants are the node \textit{Edges}, that has to be selected due to the mandatory marker, and \textit{Algorithms} that is marked optional.
+It's childs are the node \textit{Edges}, that has to be selected due to the mandatory marker, and \textit{Algorithms} that is marked optional.
 The implemented edge types are \textit{Directed} and \textit{Undirected} from which exactly one has to be chosen as they are mutually exclusive.
@@
 \subsection{Product configuration}
-The variability of a product line is represented by its feature model, which itself is a set of features with specific interrelations.
+The variability of a product line is represented by it's feature model, which itself is a set of features with specific interrelations.
 The process of configuration of a product line describes the steps to derive a product from the product line.
@@
 The interrelations of the features restrict the possible combinations of features resulting in a \textit{valid} configuration.
-If only one of the requirements from the interrelations between the features is not met, no product can be created and the configuration as such is considered \textit{invalid}.
-
-During configuration a user selects or deselects features to his needs.
-This process requires a lot of domain knowledge on the one hand and detailed information about the implementation of each single feature on the other.
-With growing numbers of features and thus growing numbers of possible products configuration requires more effort.
-However, the even greater problem arises from the possible interactions and interrelations of features, which one has to keep track of during configuration.
-The automatic selection or deselection of a features doe to propagation of a made selection always results in a valid configuration.
-Nevertheless, the propagated selections can be confusing for the user.
+If only one of the requirements from the interrelations between the features is validated, no product can be created and the configuration as such is considered \textit{invalid}.
+For automatic detection of validity, check the next section.
 
@@
 
-\subsection{Satisfiability}
-%TODO: rausschmeißen?
-A feature model can be expressed as a propositional statement. The mapping between the individual groups (sub-trees) and the corresponding propositional expression is shown in the following list:
+During configuration a user selects or deselects features to his needs.
+This process requires a lot of domain knowledge on the one hand and detailed information about the implementation of each single feature on the other.
+With growing numbers of features and thus growing numbers of possible products, configuration requires more effort.
+However, the even greater problem arises from the possible interactions and interrelations of features, which one has to keep track of during configuration.
 
-{\color{red}TODO: Rules for
-\begin{itemize}
-	\item Or
-	\item Alternative
-	\item And
-\end{itemize}
-}
-These particular groups are joined via a logical \textit{AND}. For the example feature model shown in Figure~\ref{img-fm} the corresponding propositional expression is as follows:
-\begin{equation}
-\begin{split}
-	GraphLibrary\ \wedge\ Edges\\
-	\wedge\ ((Directed\ \wedge \neg Undirected)\\
-	\vee (\neg Directed\ \wedge\ Undirected))
-\end{split}
-\end{equation}\\
+For all the interrelations of features which are contained within the feature model, an automated observation of the resulting constraints supports configuration.
+It does so by checking for satisfiability after each change in the configuration.
 
-As the feature model not only contains the feature tree, but also additional constraints, these constraints have to be considered in the boolean expression representing the complete feature model.
-They can be linked to one another via logical \textit{AND}s.
-The connection to the previously created propositional expression of the feature tree is also made through a logical \textit{AND}.
-Thus, the complete resulting propositional expression for the feature model shown in Figure~\ref{img-fm} is:
-\begin{equation}
-\begin{split}
-	GraphLibrary\ \wedge\ Edges\\
-	\wedge\ ((Directed\ \wedge \neg Undirected)\\
-	\vee (\neg Directed\ \wedge\ Undirected))\\
-	\wedge\ (Algorithms\ \Rightarrow\ (Number\ \vee\ Cycle))\\
-	\wedge\ (Cycle\ \Rightarrow\ Directed)
-\end{split}
-\end{equation}\\
-This formalism allows a configuration to be checked for validity.
-To do so each selected feature is appended with a logical \textit{AND} and each specifically unselected feature is also appended with a logical \textit{AND} but gets negated.
-The resulting expression is then evaluated by a SAT-solver to check for satisfiability.
+\subsection{Satisfiability} \label{ch:sat}
+During creation of the feature model as well as during the configuration of a product, validity must always be taken care of.
+Validity in this context is described as the satisfiability of the corresponding propositional expression.
+
+The formalism of propositional expressions (see Section~\ref{ch:fm} allows feature models and configurations to be checked for validity.
+The propositional expression of a (partial) configuration is created on the basis of the propositional expression of the underlying feature model.
+Each selected feature is appended with a logical \textit{AND} and each specifically unselected feature is also appended with a logical \textit{AND} but gets negated.
+The resulting expression is then evaluated by a SAT-solver to check for satisfiability \cite{sat-solve}.
+
 Even during configuration this process can be applied to check for invalid partial configurations after each decision.
+If a partial configuration reduces the valid choices in a single group to a single one, it can be made automatically.
+This is called \textit{propagation}.
+The automatic selection or deselection of a features due to propagation of a made selection always results in a valid configuration.
+Nevertheless the propagated selections can be confusing for the user.

### 2016-03-28 chapters/concept.tex
Scenario part 1/2 and small grammar fixes
better integration of the satisfiability section

@@
-%unstructured product line $\rightarrow$ generated feature model $\rightarrow$ %optimizing (via SAT-solver?) $\rightarrow$ domain knowledge of an expert %$\Rightarrow$ Questionnaire $\rightarrow$ Feature model + Questionnaire %$\Rightarrow$ Product (variant)\\
-
 This chapter describes the general workflow we aim to archive within this work.
@@
 The two major steps of extraction of the feature model and the creation and usage of the questionnaire are described in detail in the following sections.
+As a final result of these steps stands a product targeting the users needs.
+Supporting the process towards that result is what we aimed at with this work.
 
 \subsection{Extraction of a Feature Model}
-Out of the given structure we extract the hierarchies of the features as well as additional dependencies.
+Out of the given structure of the source code base we extract the hierarchies of the features as well as additional dependencies.
 These are the input for the automated generation of a feature model.
@@
 
-The extracted feature model is also used in the following step of configuration. There, it visualizes the interrelations of the features and supports the understanding of the configuration steps.
+In each step of the creation of the feature model, e.g.
+after adding a feature or constraint to the feature model, it is checked by a SAT-solver to avoid creating an invalid feature model which has no valid configurations (see section~\ref{ch:sat}).
+The extracted feature model is also used in the following step of configuration.
+There, it visualizes the interrelations of the features and supports the understanding of the configuration steps.
 
@@
 Our work therefore introduces a set of tools to easily integrate such a questionnaire.
-The following paragraphs will give an overview over the the possible definitions of a questionnaire.
+The following paragraphs will give an overview over the possible definitions of a questionnaire.
 
@@
 
-%TODO: Am ende kommt ein konfiguriertes Produkt raus.
+This allows for experts to design a questionnaire in such a way, that it can guide a user without specific domain knowledge throughout the whole process of configuration.
+Through just answering questions concerning his specific use-case the user takes all necessary decisions.
+After he completes the questionnaire, our tool maps his answers to a complete configuration, which is then applied to the existing code artifacts.
+Finally, a working product is the result.

### 2016-03-28 chapters/conclusion.tex
slight restructuring
TODOs added
better integration of the satisfiability section

@@
-\subsection{Conclusion}
 This is where the work is concluded.
@@
 
-\subsection{Future Work}
 Here will be a summary of the new questions that were raised in this work.
@@
 Particularly the problems we encountered and couldn't solve with our concept and why will be pointed out and first approaches will be suggested.
+
+%TODO: research questions
+In this work we aim at finding a way to support the process of configuring a software product line. To do so, we firstly introduce feature models as formalism
+
+%TODO: wann ist es sinnvoll, wann nicht?
+
+%TODO: ist das auf andere Projekte übertragbar? Was sind Voraussetzungen?
+
+%TODO: Threats to Validity

### 2016-03-28 chapters/background.tex
conclusion added, references included

@@
 One of their benefits is the visualization as a feature diagram, providing an overview of the containing features, and their hierarchy and dependencies.
-In addition, it classifies the features and their dependencies by Ordinality (Optional/mandatory), logical operator (Disjunction/exclusive disjunction) and whether it is abstract or concrete.
+In addition, it classifies the features and their dependencies by ordinality (optional/mandatory), logical operator (disjunction/exclusive disjunction) and whether it is abstract or concrete.
 Furthermore, it contains all information needed to provide a configuration of Features and its validation.
 
-Although feature models can be represented as a propositional expression in CNF, it is typically represented in form of a feature diagram.
+Although feature models can be represented as a propositional expression in CNF, it is typically represented in form of a feature diagram \cite{fmgp}.
 The feature diagram is structured as a tree.
@@
 The process of configuration of a product line describes the steps to derive a product from the product line.
-To archive this, a user has to select a subset of all the possible features within the product line to meet his requirements.
+To archive this, a user has to select a subset of all the possible features within the product line to meet his requirements \cite{vrt}.
 However, not all subsets of features result in a valid product.
@@
 With growing numbers of features and thus growing numbers of possible products, configuration requires more effort.
-However, the even greater problem arises from the possible interactions and interrelations of features, which one has to keep track of during configuration.
+However, the even greater problem arises from the possible interactions and interrelations of features, which one has to keep track of during configuration \cite{sple-fpt}.
 

### 2016-03-28 chapters/conclusion.tex
conclusion added, references included

@@
-This is where the work is concluded.
-In this section there will be a description of the way we did things and the experiences we made during it.
-An emphasis will be on the insights and the findings from the scenarios will get outlined.
+%TODO: research questions
 
-Here will be a summary of the new questions that were raised in this work.
-Also there will be topics for further research.
-Particularly the problems we encountered and couldn't solve with our concept and why will be pointed out and first approaches will be suggested.
+In this work we aim at finding a way to support the process of configuring an existing software product line to generate an actual product.
 
-%TODO: research questions
-In this work we aim at finding a way to support the process of configuring a software product line. To do so, we firstly introduce feature models as formalism
+To do so, we firstly use feature models as formalism to structure the existing code artifacts.
+The feature model gets filled with the information we get from analyzing the structure and conventions of the existing source code.
+The resulting feature model contains every code artifact as a feature and also includes the constraints and restrictions.
+
+We also introduce a questionnaire to support the configuration of a product from the given product line.
+A questionnaire needs to be designed carefully by the developers or experts on the domain of the product line.
+It allows a mapping between answers to simple questions and actual features of the product line.
+With this method, a user doesn't have to undergo the process of configuration in the sense of (un-)selecting a specific set of features.
+Instead he only has to answer questions according to his use case to do the configuration of his specific product.
+As the tool uses the underlying FeatureIDE, it also makes use of it's functions, e.g.
+validity checks.
+This additionally supports the usability and correctness of the whole process.
 
 %TODO: wann ist es sinnvoll, wann nicht?
+%TODO: ist das auf andere Projekte übertragbar? Was sind Voraussetzungen?
+%TODO: Threats to Validity
 
-%TODO: ist das auf andere Projekte übertragbar? Was sind Voraussetzungen?
+To make meaningful use of the tools introduced in this work, one would at least need a software which is structured in a ``feature-like'' manner.
+This structure has to be in a way that allows a feature model to be extracted from it.
+Alternatively, this first step can be skipped, if a feature model already exists for the given software product line.
 
-%TODO: Threats to Validity
+Also, the features have to have some kind of interrelations that allows abstract questions to map to them.
+If that is not the case, the questionnaire degenerates to a simple (un-) selection of each feature.

### 2016-03-28 chapters/intro.tex
conclusion added, references included

@@
 % and "HIS" in caps to complete the first word.
-Developing feature oriented, although bringing with it some overhead, facilitates the creation of software when it is planned on custom tailoring it for a multiple number of clients.
+Developing feature oriented, although bringing with it some overhead, facilitates the creation of software when it is planned on custom tailoring it for a multiple number of clients \cite{spl-pp}.
 Feature oriented means developing and maintaining single features that can be combined with others to create a whole product.
@@
 By developing with a feature-oriented approach the configuration of a single variant can be done by selecting the features a customer needs, automatically including its dependencies.
-The configuration is based on a Feature Model, that defines the available Features and its relations to one another.
+The configuration is based on a feature model, that defines the available features and its relations to one another.
 A feature model documents the features of a product line and their relationships\cite{fospl}.
@@
 Although the feature configuration gives developers the ability to create custom variants, there still has to be a consultant explaining the features to the customer, trying to figure out his current and future needs.
-As the software grows and gets more features, this process gets difficult, as one can no longer explain all the features, but you still have to figure out if the customer needs them or not.
-This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
+As the software grows and gets more features, this process gets difficult, as one can no longer explain all the features, but still has to figure out if the customer needs them or not.
+This paper tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
 

### 2016-03-28 chapters/conclusion.tex
todos are now in the pdf

@@
 With this method, a user doesn't have to undergo the process of configuration in the sense of (un-)selecting a specific set of features.
-Instead he only has to answer questions according to his use case to do the configuration of his specific product.
-As the tool uses the underlying FeatureIDE, it also makes use of it's functions, e.g.
+Instead, he only has to answer questions according to his use case to do the configuration of his specific product.
+As the tool uses the underlying FeatureIDE, it also makes use of its functions, e.g.
 validity checks.

### 2016-03-29 chapters/concept.tex
conclusion added, references included
Added reviews part 1/2

@@
-This chapter describes the general workflow we aim to archive within this work.
+This chapter describes the general workflow we propose within this work.
 This workflow can be seen in Figure~\ref{img-workflow}.
 To start off, some kind of software product line is required.
-It's source code has to be structured in a way that allows for an algorithm to recognize the individual features as well as their interrelations, especially the hierarchical dependencies.
+It's source code has to be structured in a way that allows for an algorithm to recognize the individual features as well as their interrelations, as these can be very costly to implement by hand.
+
+{\color{red} Pfeil von Fragebogen zu Generator sollte zu der Selektion zeigen.}
 
@@
 As a final result of these steps stands a product targeting the users needs.
-Supporting the process towards that result is what we aimed at with this work.
 
@@
 This allows for overview over the product line and it's variability.
-During our efforts to implement an automated generation of a feature model we encounter some problems for which we have to find solutions/workarounds.
+During our efforts to implement an automated generation of a feature model we encounter some problems for which we have to find solutions or workarounds.
 
-The first problem consists of finding the structures of the given source code and processing them algorithmically.
+The first challenge consists of finding the structures of the given source code and processing them programmatically.
 Most software complies to conventions regarding the naming and structuring of directories.
 We try to make use of these conventions.
-But as they are just conventions and not rules, in most source code one will find violations of the conventions.
+However, in most source code there are violations within their own conventions.
 Instead of interrupting the whole process, we implement error handling.
@@
 
-Another error we found is one ore more features having a parent feature which doesn't exist as a code artifact itself.
+Another error we found is one or more features having a parent feature which doesn't exist as a code artifact itself.
 Thus, the parent feature doesn't exists in the feature model and it's child features can't be placed in the hierarchy in the correct place.
-To still include these features in the feature model we create an abstract feature for the parent feature.
+To still include these features in the feature model we create an {\color{red}abstract feature (Zitat)} for the parent feature.
 The abstract feature is a direct child of the root feature.
-But as it doesn't have any describing code, it only has a name and no additional descriptive details.
+As it doesn't have any describing code, it only has a name and no additional descriptive details.
 
 In each step of the creation of the feature model, e.g.
-after adding a feature or constraint to the feature model, it is checked by a SAT-solver to avoid creating an invalid feature model which has no valid configurations (see section~\ref{ch:sat}).
+after adding a feature or constraint to the feature model, it is checked by a SAT-solver to avoid creating an invalid feature model (represented by a void object) which has no valid configurations (see section~\ref{ch:sat}).
 The extracted feature model is also used in the following step of configuration.
@@
 
-This work therefore introduces a method to allow experts to apply their knowledge and understanding to a whole product line during the development.
-Thus, users are enabled to draw on this knowledge whenever a configuration is taking place.
+This work introduces a method allowing experts to apply their knowledge and understanding to a whole product line during the development.
+Whenever a variation is configured using the questionnaire, the user benefits from the invested domain knowledge.
 
-In this work, we made the decision to use a questionnaire-based approach.
+In this work, we made the decision to use a questionnaire-based approach \cite{qbvm}.
 In the progress of implementation, experts also design a questionnaire.
@@
 The user only has to decide between the possible answers presented to him in the questionnaire to best fit to his use-case.
-Internally the selected answers are mapped to a specified (un-)selection of features so the user avoids the hassle of considering implementation-details of each feature.
+Internally the selected answers are mapped to a specified (de-)selection of features.
+This way the user avoids the hassle of considering implementation-details of each feature.
 This effectively redesigns the process of configuration in such a way, that a user is independent of the knowledge about the details of the implementation and can focus on tailoring the product line to his specific use-case.
 
-This highly depends on the implementation of the questionnaire during development.
+\subsection{Questionnaire Implementation}
+
+The quality of the resulting variation highly depends on the implementation of the questionnaire during development.
 Our work therefore introduces a set of tools to easily integrate such a questionnaire.
@@
 
+{\color{red} TODO: add screenshots}
+
 Each page of the questionnaire is defined independently.
-It always contains at least a Question and more then one possible answer.
+It always contains at least a question and more than one possible answer.
 The answers can be grouped analogous to the grouping of features in a feature model: \textit{or} (at least one answer has to be selected), \textit{alternative} (exactly one answer has to be selected) and \textit{and} (any number of answers can be selected).
 
-Each answer internally has a mapping to a set of features. This set of features defines which features are selected or specifically unselected in the case of that answer being chosen by the user.
+Each answer internally has a mapping to a set of features. In the case a specific answer is chosen, the corresponding features are selected or deselected as specified.
 
-Each answer can also have an indicator to define which page of the questionnaire is to be displayed next.
+Each answer can also have an indicator to define which page of the questionnaire should be displayed next.
 An answer can also indicate the end of the questionnaire.
@@
 To archive easy integration we decided for a definition in XML.
-We defined the necessary tags to create a questionnaire which are displayed in figure~\ref{fig:xmlFigure}.
+We defined the necessary tags to create a questionnaire which are displayed in Figure~\ref{fig:xmlFigure}.
 

### 2016-03-29 chapters/conclusion.tex
Added reviews part 1/2

@@
 
-In this work we aim at finding a way to support the process of configuring an existing software product line to generate an actual product.
+{\color{red}Ihr geht hier in die falsche Richtung. Schreibt einfach was jetzt geht, ihr bracht hier nicht zu diskutieren was notwendig ist oder so (wie z.b. im letzten absatz)}
 
-To do so, we firstly use feature models as formalism to structure the existing code artifacts.
+In this work we propose a questionnaire-based approach to support the process of configuring an existing software product line to generate an actual product.
+To do so, we use feature models as formalism to structure the existing code artifacts.
 The feature model gets filled with the information we get from analyzing the structure and conventions of the existing source code.
@@
 It allows a mapping between answers to simple questions and actual features of the product line.
-With this method, a user doesn't have to undergo the process of configuration in the sense of (un-)selecting a specific set of features.
-Instead, he only has to answer questions according to his use case to do the configuration of his specific product.
-As the tool uses the underlying FeatureIDE, it also makes use of its functions, e.g.
-validity checks.
+With this method, a user doesn't have to undergo the process of configuration in the sense of \mbox{(de-)selecting} a specific set of features.
+Instead, the user only has to answer questions according to its use case to do the configuration of his specific product.
+As the tool uses the underlying FeatureIDE, it also makes use of its functions, such as validity checks.
 This additionally supports the usability and correctness of the whole process.
@@
 
-To make meaningful use of the tools introduced in this work, one would at least need a software which is structured in a ``feature-like'' manner.
+To make meaningful use of the tools introduced in this work, a developer would at least need a software which is structured in a ``feature-like'' manner.
 This structure has to be in a way that allows a feature model to be extracted from it.
@@
 
-Also, the features have to have some kind of interrelations that allows abstract questions to map to them.
+Also, the features need to have some kind of interrelations that allows abstract questions to map to them.
 If that is not the case, the questionnaire degenerates to a simple (un-) selection of each feature.

### 2016-03-29 chapters/scenarios.tex
todos are now in the pdf
Added reviews part 1/2

@@
-In the fallowing chapter the workflow described in Chapter~\ref{ch:workflow} is carried out based on the current project status of \textit{Odoo}.
-At first a feature model is generated based on the naming conventions of the project folders and the configuration files contained therein.
+{\color{red} erstmal beschreiben was odoo ist und warum ihr euren ansatz darauf anwenden wollt und könnt dann bitte auch noch erklären wie das projekt strukturiert is, wie groß es ist, wie viele module es gibt etc.referenz zur odoo webseite oder repository}
+
+In the fallowing chapter the workflow described in chapter~\ref{ch:workflow} is carried out based on the current project status of \textit{Odoo}.
+At first, a feature model is generated based on the naming conventions of the project folders and the configuration files contained therein.
 Afterwards the feature model is corrected from any errors that occurred during the generation process.
 The resulting model combined with domain knowledge allows for the creation of a questionnaire that takes a minimum of choices to configure a custom tailored application.
+
+{\color{red} bitte die komplette struktur vorab klären}
 
@@
 These files contain a description of the feature, a name, that doesn't always match with the folder name and the dependencies that are required for this feature to work.
-By first creating a list of all features based on the folder names, one can match them to the names inside of the configuration files.
+By first creating a list of all features based on the folder names, we can match them to the names inside of the configuration files.
 At this point we realize, that there are some conflicts in the naming of the 261 features.
@@
 
+{\color{red}TODO: Fragebogen}
+
+{\color{red}TODO: Auswertung}
+
 %TODO: Auswertung
-TODO:
 
-Also state how some of the questions and their mapping in the questionnaire were developed.
+%Also state how some of the questions and their mapping in the questionnaire were developed.
 
-Finally, show the process of configuration through running a fictinal user over the questionnaire and document his decisions as well as the resulting configurations.
+%Finally, show the process of configuration through running a fictinal user over the questionnaire and document his decisions as well as the resulting configurations.
 

### 2016-03-29 chapters/background.tex
Added/solved reviews part 2/2

--- 2016-03-28 chapters/background.tex
@@
-In the scope of supporting the configuration of a given product line some specific tools and techniques are used.
-This section gives an overview of what is used in this work to archive a simplification of the workflow from a "product line"-like source code base to a final product.
+In the scope of supporting the configuration of a given product line some specific tools and techniques are used. This section gives an overview about the used techniques.
 
 \subsection{Feature Models} \label{ch:fm}
-Feature models are multi-purpose structure for product lines. 
 \begin{figure}
@@
 \end{figure}
+
+Feature models are a multi-purpose structure for product lines.
 One of their benefits is the visualization as a feature diagram, providing an overview of the containing features, and their hierarchy and dependencies.
-In addition, it classifies the features and their dependencies by Ordinality (Optional/mandatory), logical operator (Disjunction/exclusive disjunction) and whether it is abstract or concrete.
-Furthermore, it contains all information needed to provide a configuration of Features and its validation.
+In addition, it classifies the features and their dependencies by ordinality, logical operator and whether it is abstract or concrete.
+Furthermore, it contains all information needed to provide a configuration of features and its validation.
+A configuration, or chosen set of features, is valid if there are no contradictions in the models dependencies or logical operators.
 
-Although feature models can be represented as a propositional expression in CNF, it is typically represented in form of a feature diagram.
-The feature diagram is structured as a tree.
+There are two main representations of feature models.
+The first approach is a propositional expression, which is a type of syntactic formula often used in propositional logic.
+However feature models are typically visualized in form of a feature diagram, which is structured as a tree \cite{fmgp}.
 In that manner feature models map the hierarchy of features.
 The possible relationships of features with a common parent feature are \textit{or}, \textit{alternative} and \textit{and}.
+All child features beneath a parent feature have the same relationship and therefore form a \textit{group}.
 In the case of an \textit{or}-group, at least one of the child features has to be selected if the parent feature is selected.
 Within an \textit{alternative}-group exactly one of the child feature has to be selected if the parent feature is selected.
-When grouped with an \textit{and}-relation, any number of child features can be selected, if the parent feature is selected.
-In addition, child features in an \textit{and}-group can be marked as either mandatory or optional.
+When features are grouped with an \textit{and}-relation, they are marked as either mandatory or optional.
+If the parent feature of an \textit{and}-group is selected, any number of optional marked features can be selected.
+Features marked as mandatory have to be selected.
 As features' relations may be of higher complexity than just parent-child relations additional constraints can be noted within a feature model.
@@
 
-Figure~\ref{img-fm} shows an example of a simple feature model.
+In Figure~\ref{img-fm} we demonstrate an example of a simple feature model.
 The node \textit{GraphLibrary} is the root feature.
-It's childs are the node \textit{Edges}, that has to be selected due to the mandatory marker, and \textit{Algorithms} that is marked optional.
+It's childs are the node \textit{Edges}, that has to be selected due to the mandatory property, and \textit{Algorithms} that is marked optional.
 The implemented edge types are \textit{Directed} and \textit{Undirected} from which exactly one has to be chosen as they are mutually exclusive.
-From the algorithms at least one has to be chosen whenever \textit{Algorithms} is selected.
-The constraint beneath Figure~\ref{img-fm} implies that if the feature \textit{Cycle} is selected, the edge type needs to be directed.
+From the algorithms at least one feature has to be chosen whenever \textit{Algorithms} is selected.
+The constraint at the bottom of Figure~\ref{img-fm} implies that if the feature \textit{Cycle} is selected, the edge type needs to be directed.
 
-\subsection{Product configuration}
+\subsection{Product Configuration}
 The variability of a product line is represented by it's feature model, which itself is a set of features with specific interrelations.
-The process of configuration of a product line describes the steps to derive a product from the product line.
-To archive this, a user has to select a subset of all the possible features within the product line to meet his requirements.
+The configuration process of a product line describes the steps to derive a product from the product line.
+To archive this, a user has to select a subset of all the possible features within the product line to meet his requirements \cite{vrt}{\color{red} (nicht in Literaturliste)}.
 However, not all subsets of features result in a valid product.
 The interrelations of the features restrict the possible combinations of features resulting in a \textit{valid} configuration.
-If only one of the requirements from the interrelations between the features is validated, no product can be created and the configuration as such is considered \textit{invalid}.
-For automatic detection of validity, check the next section.
+{\color{red} Bin mir nicht sicher, was du damit sagen willst...
+umformulieren?} If only one of the requirements from the interrelations between the features is validated, no product can be created and the configuration as such is considered \textit{invalid}.
+For an automatic validity check, see the next section.
 
@@
 A \textit{valid} partial configuration can be useful, as it narrows down the number of possible resulting variations and choices left to make.
-
-During configuration a user selects or deselects features to his needs.
-This process requires a lot of domain knowledge on the one hand and detailed information about the implementation of each single feature on the other.
-With growing numbers of features and thus growing numbers of possible products, configuration requires more effort.
-However, the even greater problem arises from the possible interactions and interrelations of features, which one has to keep track of during configuration.
-
-For all the interrelations of features which are contained within the feature model, an automated observation of the resulting constraints supports configuration.
-It does so by checking for satisfiability after each change in the configuration.
+As the aim is to achieve a valid final configuration, there has to be a valid partial configuration after every choice made.
 
@@
 
-The formalism of propositional expressions (see Section~\ref{ch:fm} allows feature models and configurations to be checked for validity.
-The propositional expression of a (partial) configuration is created on the basis of the propositional expression of the underlying feature model.
+The formalism of propositional expressions (see Section~\ref{ch:fm}) allows feature models and configurations to be checked for validity.
 Each selected feature is appended with a logical \textit{AND} and each specifically unselected feature is also appended with a logical \textit{AND} but gets negated.
 The resulting expression is then evaluated by a SAT-solver to check for satisfiability \cite{sat-solve}.
+If the expression is satisfiable the selected features make up a valid configuration.
 
 Even during configuration this process can be applied to check for invalid partial configurations after each decision.
-If a partial configuration reduces the valid choices in a single group to a single one, it can be made automatically.
+If a partial configuration reduces the valid choices in a group to a single one, this choice can be made automatically.
 This is called \textit{propagation}.
-The automatic selection or deselection of a features due to propagation of a made selection always results in a valid configuration.
-Nevertheless the propagated selections can be confusing for the user.
+The automatic selection or deselection of a features due to propagation of a made selection always results in a valid configuration \cite{fmi}.

### 2016-03-29 chapters/intro.tex
Added/solved reviews part 2/2

@@
 % and "HIS" in caps to complete the first word.
-Developing feature oriented, although bringing with it some overhead, facilitates the creation of software when it is planned on custom tailoring it for a multiple number of clients \cite{spl-pp}.
+Developing feature oriented fashion facilitates the creation of software when it is planned on custom tailoring it for a multiple number of clients \cite{spl-pp}.
 Feature oriented means developing and maintaining single features that can be combined with others to create a whole product.
-All the individual features make up a product line, whereas a subset of those features create a variant of this product.
+All the individual features make up a product line, whereas a subset of those features create a variant of this product line.
 Developing software product lines can result in a large amount of variants, when customizing the software to each customers needs.
-By developing with a feature-oriented approach the configuration of a single variant can be done by selecting the features a customer needs, automatically including its dependencies.
-The configuration is based on a feature model, that defines the available features and its relations to one another.
+By developing with a feature-oriented approach the configuration of a single variant can be done by selecting the features a customer needs.
+Often features have dependencies to one another, which can be added to a feature model to verify a configuration.
 A feature model documents the features of a product line and their relationships\cite{fospl}.
 
-Feature Models are essential structures for the feature-oriented development and later configuration of software product lines (SPL).
 There are projects being developed in a feature-oriented manner, but don't have a feature model yet.
-Implementing it on top of a given Project can result in a complex task due to the amount of its features and the constraints between them.
+Implementing it on top of a given project can result in a complex task due to the amount of its features and the constraints between them.
 Nevertheless, the benefits of a correct feature model justify the effort to extract one out of a live project.
-This work aims at automatically generating it out of descriptive files and naming conventions, to simplify a big part of the feature model creation.
+To simplify a big part of the feature model creation, this work aims at automatically generating it out of descriptive files and naming conventions.
 
@@
 
+For the implementation of the feature extraction and the questionnaire, we used the eclipse plugin FeatureIDE.
 FeatureIDE is an open source IDE for feature-oriented-software development.
@@
 This includes the logic behind configurations, data structures and the visualization and processing of feature models.
-The underlying Eclipse enables us to implement the feature extraction and the questionnaire as a plugin.
 
-This work demonstrates the feature model extraction and questionnaire creation based on a real life Project.
-The Project, an open source ERP system called \textit{Odoo}\footnote{https://www.odoo.com/} is predestined to be developed feature-oriented due to a huge amount of features and complex constraints.
+In the second part of this work, we demonstrate the feature-model extraction and questionnaire creation based on a real life project.
+The project, an open source ERP system called \textit{Odoo}\footnote{https://www.odoo.com/} is predestined to be developed feature-oriented due to a huge amount of features and complex constraints.
 It is currently being developed and structured feature oriented, although it doesn't contain a feature model yet.
@@
 \begin{itemize}
-\item Automatic feature model generation based on descriptive files and naming conventions as a foundation for the thereon based questionnaire.
-\item Eclipse plugin, that enables the creation of a questionnaire based on a configuration file and the associated feature model.
+\item Automatic feature-model generation based on descriptive files and naming conventions as a foundation for the thereon based questionnaire.
+\item We introduce an Eclipse plugin, that enables the creation of a questionnaire based on a configuration file and the associated feature model.
 The liberties of the configuration file specification allows very personalized questionnaires.
-\item The questionnaire changes as choices are made based on the logic behind the configuration file and the dependencies of the feature model.
+\item The questionnaire reacts to the choices made by reacting differently on each questions outcome.
 This enables a responsive questionnaire that prevents unnecessary questions.
-\item Exiting the questionnaire always results in a valid configured variant to always ensure a valid configuration.
+In addition, every choice made creates a valid partial configuration, even if the questionnaire is exited early.
+\item Illustration of the described workflow by applying it to a real world project.
 \end{itemize}

### 2016-03-29 chapters/background.tex
refined conclusion, minor fixes

@@
 The configuration process of a product line describes the steps to derive a product from the product line.
-To archive this, a user has to select a subset of all the possible features within the product line to meet his requirements \cite{vrt}{\color{red} (nicht in Literaturliste)}.
+To archive this, a user has to select a subset of all the possible features within the product line to meet his requirements \cite{vrt}.
 However, not all subsets of features result in a valid product.
-The interrelations of the features restrict the possible combinations of features resulting in a \textit{valid} configuration.
-{\color{red} Bin mir nicht sicher, was du damit sagen willst...
-umformulieren?} If only one of the requirements from the interrelations between the features is validated, no product can be created and the configuration as such is considered \textit{invalid}.
+The interrelations of the features restrict the possible combinations of features.
+Thus, not all arbitrary cobinations of features result in a \textit{valid} configuration.
+If only one of the requirements from the interrelations between the features is validated, no product can be created and the configuration as such is considered \textit{invalid}.
 For an automatic validity check, see the next section.

### 2016-03-29 chapters/concept.tex
Added/solved reviews part 2/2
refined conclusion, minor fixes

@@
 This chapter describes the general workflow we propose within this work.
-This workflow can be seen in Figure~\ref{img-workflow}.
+This can be seen in Figure~\ref{img-workflow}.
 To start off, some kind of software product line is required.
 It's source code has to be structured in a way that allows for an algorithm to recognize the individual features as well as their interrelations, as these can be very costly to implement by hand.
-
-{\color{red} Pfeil von Fragebogen zu Generator sollte zu der Selektion zeigen.}
 
@@
 Thus, the parent feature doesn't exists in the feature model and it's child features can't be placed in the hierarchy in the correct place.
-To still include these features in the feature model we create an {\color{red}abstract feature (Zitat)} for the parent feature.
+To still include these features in the feature model we create an {\color{red}abstract feature (Zitat: fospl, page 35, line 10)} for the parent feature.
 The abstract feature is a direct child of the root feature.

### 2016-03-29 chapters/conclusion.tex
refined conclusion, minor fixes

@@
 To do so, we use feature models as formalism to structure the existing code artifacts.
-The feature model gets filled with the information we get from analyzing the structure and conventions of the existing source code.
+The feature model automatically gets filled with the information we get from analyzing the structure and conventions of the existing source code.
 The resulting feature model contains every code artifact as a feature and also includes the constraints and restrictions.
 
-We also introduce a questionnaire to support the configuration of a product from the given product line.
+We also propose a questionnaire to support the configuration of a product from the given product line.
+We introduce definitions in XML, which allow for creation of questionnaires specifically designed for configuration.
 A questionnaire needs to be designed carefully by the developers or experts on the domain of the product line.
@@
 
-%TODO: wann ist es sinnvoll, wann nicht?
-%TODO: ist das auf andere Projekte übertragbar? Was sind Voraussetzungen?
-%TODO: Threats to Validity
-
-To make meaningful use of the tools introduced in this work, a developer would at least need a software which is structured in a ``feature-like'' manner.
-This structure has to be in a way that allows a feature model to be extracted from it.
-Alternatively, this first step can be skipped, if a feature model already exists for the given software product line.
-
-Also, the features need to have some kind of interrelations that allows abstract questions to map to them.
-If that is not the case, the questionnaire degenerates to a simple (un-) selection of each feature.
+For the exapmle of \textit{Odoo}, we were able to extract a feature model from the code.
+We also designed an examplary questionnaire and ran it with a simulated test user.
+This test user had a certain use case, which we were able to apply to the questionnaire through just answering the presented questions.
+As a result we got a custom tailored version of \textit{Odoo} for our test user.

### 2016-03-31 chapters/concept.tex
minor fixes
table corrected

@@
 
+%Cite: fospl, page 35, line 10
 Another error we found is one or more features having a parent feature which doesn't exist as a code artifact itself.
 Thus, the parent feature doesn't exists in the feature model and it's child features can't be placed in the hierarchy in the correct place.
-To still include these features in the feature model we create an {\color{red}abstract feature (Zitat: fospl, page 35, line 10)} for the parent feature.
+To still include these features in the feature model we create an abstract feature \cite{fospl} for the parent feature.
 The abstract feature is a direct child of the root feature.
@@
 \begin{figure}[H]
-\begin{tabulary}{\linewidth}{LLL}
-\textbf{Tag} & \textbf{attributes} & \textbf{child tags}\\
+\begin{tabulary}{\linewidth}{| L | L | L |}
 	\hline
-configurationSurvey & & projectName, section, page\\
-section & id & name, description\\
-page & id, sectionId & question, answers\\
-answers & type & answer\\
-answer & nextPageId & label, description, dependencies\\
-dependencies & & feature\\
-feature & selection & \\
-\end{tabulary}\vspace{2.5em}
+	\textbf{Tag} 		& \textbf{\mbox{Attributes}} & \textbf{Child tags}	\\ \hline
+
+	configurationSurvey & 				& projectName, section, page		\\ \hline
+	section 			& id 			& name, description					\\ \hline
+	page 				& id, sectionId & question, answers					\\ \hline
+	answers 			& type 			& answer							\\ \hline
+	answer 				& nextPageId 	& label, description, dependencies	\\ \hline
+	dependencies		& 				& feature							\\ \hline
+	feature 			& selection 	& 									\\ \hline
+\end{tabulary}
+\caption{Table with the XML element structure}
+\label{tab-xmlelements}
 \end{figure}

### 2016-03-31 chapters/abstract.tex
todos are now in the pdf
rewrote the abstract

--- 2016-02-03 chapters/abstract.tex
@@
 Variability management is an essential part of working on product lines.
-This paper considers existing methods of configuration and tries to come up with a better alternative based on questionnaires to enable users or customers to configure a product on their own and to allow experts to design the questionnaires according to their domain knowledge.
-To further simplify the process of product configuration out of software product-lines, feature models are used to describe the set of features and constraints contained in a given software product-line.
-This paper proposes a method for automatically generating feature models out of descriptive files and naming conventions.
+Feature models are an established tool to describe the set of features and constraints contained in a given software product-line, thus showing the variability.
+Feature models also facilitate configuration of product lines.
+However, for most software product lines there exists no feature model.
+This paper proposes a method for automatically generating feature models out of the structure of given source code and naming conventions.
+
+Furthermore, an alternative method of configuration based on questionnaires is developed in this work.
+It enables users or customers to configure a product on their own.
+Also, it allows experts to design the questionnaires according to their domain knowledge during implementation of the product line.

### 2016-03-31 chapters/related.tex
Related Work added

Several techniques for synthesising Feature Models from a set of configurations, constraints, or even publicly available product descriptions found online have been proposed \cite{zhang2013mining, becan2014webfml, davril2013feature}. These techniques require very few informations of the source, but therefore can only create limited Feature Models. Furthermore they cannot be applied in our context, as they assume the availability of formal and complete descriptions of configurations and constraints. Therefore we developed a new extraction method that relies on set project structure and conventions.

Heymans et al. \cite{davril2013feature} presented an approach to generate a feature model out of a product description. This approach equals the folder names we are provided with, although Heymans lacks the hierarchy of those features, which have to be extracted by mining associations. As we get the hierarchy out of the configuration files we already have all information needed. This approach could be used in later work to handle naming conflicts or missing information.

The approach from La Rosa et al. \cite{qbvm} presents some techniques to configure a variable system based on questionnaire models and domain constraints. The main parts can be applied to feature models, although barely referenced them. Therefore they did not include all of the different logic that features can have, simplifying it in a way. They did nevertheless present a technique to detect circular dependencies and contradictory constraints, which was not part of this work, but could be a focus for further improvements.

### 2016-03-31 chapters/scenarios.tex
Related Work added

@@
-{\color{red} erstmal beschreiben was odoo ist und warum ihr euren ansatz darauf anwenden wollt und könnt dann bitte auch noch erklären wie das projekt strukturiert is, wie groß es ist, wie viele module es gibt etc.referenz zur odoo webseite oder repository}
+{\color{red} TODO: erstmal beschreiben was odoo ist und warum ihr euren ansatz darauf anwenden wollt und koennt dann bitte auch noch erklaeren wie das projekt strukturiert is, wie groß es ist, wie viele module es gibt etc.}
 
@@
 
-{\color{red} bitte die komplette struktur vorab klären}
+{\color{red} TODO: Bitte die komplette struktur vorab klaeren}
 

### 2016-03-31 chapters/scenarios.tex
Remarks fixed in Chapter 4

@@
-{\color{red} TODO: erstmal beschreiben was odoo ist und warum ihr euren ansatz darauf anwenden wollt und koennt dann bitte auch noch erklaeren wie das projekt strukturiert is, wie groß es ist, wie viele module es gibt etc.}
+In the fallowing chapter the workflow described in chapter~\ref{ch:workflow} is carried out based on the current project status of \textit{Odoo}\footnote{https://www.odoo.com/}.
+\textit{Odoo} (formerly known as OpenERP) is a suite of \textit{open-source}\footnote{https://github.com/odoo/odoo} enterprise applications, targeting companies of all sizes.
+As each costumer needs different functionalities from \textit{Odoo}, the product variations can be very different in size and target use.
+Besides them researching in the field of easing their product configuration process, this project suits our workflows requirements.
 
-In the fallowing chapter the workflow described in chapter~\ref{ch:workflow} is carried out based on the current project status of \textit{Odoo}.
+The current version of \textit{Odoo} (version 9.0, released \mbox{October 1, 2015)} has 465~contributors and over 101.200~commits.
+They have developed 266 features which are all inside of a top hierarchy folder named "addons".
+Each of them contain code as well as a configuration file named "\textunderscore\textunderscore openerp\textunderscore\textunderscore.py".
+Inside this file there are all the relevant informations for this feature, like dependencies, summaries , categories, versions and more descriptive informations.
+
 At first, a feature model is generated based on the naming conventions of the project folders and the configuration files contained therein.
@@
 
-{\color{red} TODO: Bitte die komplette struktur vorab klaeren}
-
-All the Odoo features lie inside of a folder named "addons".
+All the \textit{Odoo} features lie inside of a folder named "addons".
 The code of each feature is contained in its own folder which is named like the parent feature with a suffix of its own name.
@@
 The resulting feature model is arranged in a total of six hierarchical levels.
-Additionally, [D] constraints limit the possible valid configurations of \textit{Odoo}.
+Additionally, 196 constraints limit the possible valid configurations of \textit{Odoo}.
 

### 2016-04-04 chapters/related.tex
changes to related work implemented

@@
-Several techniques for synthesising Feature Models from a set of configurations, constraints, or even publicly available product descriptions found online have been proposed \cite{zhang2013mining, becan2014webfml, davril2013feature}.
-These techniques require very few informations of the source, but therefore can only create limited Feature Models.
+Several techniques for synthesising feature models from a set of configurations, constraints, or even publicly available product descriptions have been proposed \cite{zhang2013mining, becan2014webfml, davril2013feature}.
+These techniques assume and require very few informations of the source, but therefore can only create limited feature models.
 Furthermore they cannot be applied in our context, as they assume the availability of formal and complete descriptions of configurations and constraints.
 Therefore we developed a new extraction method that relies on set project structure and conventions.
+This leads to a feature model with a correct hierarchy, original feature names, descriptions and complete dependencies.
 
-Heymans et al.
+Davril et al.
 \cite{davril2013feature} presented an approach to generate a feature model out of a product description.
-This approach equals the folder names we are provided with, although Heymans lacks the hierarchy of those features, which have to be extracted by mining associations.
-As we get the hierarchy out of the configuration files we already have all information needed.
-This approach could be used in later work to handle naming conflicts or missing information.
+The results from this approach equal to the information given by the folder names we are provided with, although Davril et al.
+lacks the hierarchy of those features.
+They achieve the hierarchy by mining associations.
+As we get the hierarchy out of the configuration files, we already have all information needed with less effort and higher probability of a correct result.
+However, this approach could be used in later work to handle naming conflicts or missing information.
 
@@
 \cite{qbvm} presents some techniques to configure a variable system based on questionnaire models and domain constraints.
-The main parts can be applied to feature models, although barely referenced them.
-Therefore they did not include all of the different logic that features can have, simplifying it in a way.
-They did nevertheless present a technique to detect circular dependencies and contradictory constraints, which was not part of this work, but could be a focus for further improvements.
+The main parts can be applied to feature models, although this was not the focus of their work.
+Therefore they only included and-groups and did not include or-groups and alternative-groups, simplifying it in a way.
+Nevertheless, they did present a technique to detect circular dependencies and contradictory constraints, which was not part of this work, but could be a focus for further improvements.

### 2016-04-04 chapters/scenarios.tex
evaluation added to the scenario

@@
 The current version of \textit{Odoo} (version 9.0, released \mbox{October 1, 2015)} has 465~contributors and over 101.200~commits.
-They have developed 266 features which are all inside of a top hierarchy folder named "addons".
-Each of them contain code as well as a configuration file named "\textunderscore\textunderscore openerp\textunderscore\textunderscore.py".
+They have developed 266 features which are all inside of a top hierarchy folder named ``addons''.
+Each of them contain code as well as a configuration file named ``\_\_openerp\_\_.py''.
 Inside this file there are all the relevant informations for this feature, like dependencies, summaries , categories, versions and more descriptive informations.
+Inside the \textit{Odoo} repository there are also other directories, like ``doc'' for documentary files, ``setup'' for deployment scripts on various platforms and ``openerp'' with the core code.
+However, as the variability is only contained within the features, the only relevant directory for this work is ``addons''.
 
@@
 
+The choices made by the user have to be evaluated.
+This happens after each single question got answered.
+Especially the validity needs to be ensured at every time.
+Optimally, the questionnaire gets designed in such a way, that it is impossible to create an invalid configuration by just answering it.
+However, as the questionnaire itself does not get checked for validity, checking the answers adds that needed reassurance for validity.
+To check for validity, the dependencies assigned to a selected answer are checked.
+If a dependency-feature is previously unselected (undefined), it get (de-) selected according to the definition in the questionnaire.
+But if is already is in a state of (de-) selection, that doesn't match the state assigned in the questionnaire, an error occurs and warns the user of an invalid configuration.
+
+As stated in Section~\ref{ch:quest-impl}, it is possible to define a dynamic ordering of the questions within the questionnaire according to the given answer.
+The next step in evaluating the user input is looking for the correct question to be asked next.
+If there is a next question explicitly stated in the selected answer, that question gets displayed next.
+Else, if there are questions left unanswered in the questionnaire, that occur after the current questions, the question displayed next is the question following the current question in the definition.
+If there is no next question to be displayed, the questionnaire is considered finished.
+Optimally, this also results in a final configuration of a product.
+However, our design also allows for partial configurations as a result of an executed questionnaire.
+In the case of a finished configuration, this configuration gets passed to FeatureIDE, which then compiles the configured product.
+
 {\color{red}TODO: Fragebogen}
-
-{\color{red}TODO: Auswertung}
 

### 2016-04-04 chapters/scenarios.tex
Screenshot added

@@
 We applied these steps to a total of 261 folders, containing in total more than 18.800 files, extracting 306 features.
-The surplus features result from abstract features, that do not have their own folder, but are implizit in the naming.
+The surplus features result from abstract features, that do not have their own folder, but are implicit in the naming.
 The resulting feature model is arranged in a total of six hierarchical levels.
@@
 
+\begin{figure}
+	\includegraphics[width=\columnwidth]{img/img-screenshots.png}
+	\caption{Screen shots of the questionnaire dialog while configuring Odoo}
+	\label{img-screenshots}
+\end{figure}
+
 {\color{red}TODO: Fragebogen}

### 2016-04-04 chapters/scenarios.tex
added missing questionnaire usage in chapter 4

@@
 However, as the variability is only contained within the features, the only relevant directory for this work is ``addons''.
+
+\subsection{Feature Model extraction}
 
@@
 
+\subsection{Questionnaire Usage}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{img/img-screenshots.png}
+	\caption{Screen captures of the questionnaire dialog configuring an e-commerce website}
+	\label{img-screenshots}
+\end{figure}
+
 The choices made by the user have to be evaluated.
@@
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{img/img-screenshots.png}
-	\caption{Screen shots of the questionnaire dialog while configuring Odoo}
-	\label{img-screenshots}
-\end{figure}
+To check the flexibility and usability of the questionnaire, we decided to try it on a sample use case.
+As Odoo has not implemented a questionnaire of their own yet, we build one based on their website and features from the generated feature model.
+As a use case, we chose the demand for a e-commerce website for a newly created online-only shop.
+To start off, the questionnaire shown in Figure~\ref{img-screenshots} asks whether we already use any Odoo components at our company.
+If we would have pressed "Yes", we could have chosen which one and in the later steps this would be considered.
+After choosing "No", we are asked which of the Odoo topics interests us, answering it with "Websites" and "Sales".
+This brings us to a wizard page showing all of the websites we could choose.
+After selecting "eCommerce" the next page already chose "Accounting" for us, as this was one of the dependencies from the features that were selected in the background when we chose "eCommerce".
+No matter what we select on the last page, we can no longer press "next", as there is no next Page for us to configure.
+To get our configuration file we press "Finish", which we could have done any time during the configuration, generating a partial configuration.
 
-{\color{red}TODO: Fragebogen}
+The generated configuration file contains 38 features, from which 10 were selected directly and the rest as dependencies.
+This process could have been done alone with the feature tree, but that would have taken much longer, as there is no sorting and the feature names are not as descriptive as the choices from the questionnaire.
+Although we probably did not cover all possible cases in our questionnaire doe to the lack of domain knowledge, this sample shows that this use case can be handled comfortably with our questionnaire.
 

### 2016-04-04 chapters/scenarios.tex
last minor fixes

@@
 To check the flexibility and usability of the questionnaire, we decided to try it on a sample use case.
-As Odoo has not implemented a questionnaire of their own yet, we build one based on their website and features from the generated feature model.
+As \textit{Odoo} has not implemented a questionnaire of their own yet, we build one based on their website and features from the generated feature model.
 As a use case, we chose the demand for a e-commerce website for a newly created online-only shop.
-To start off, the questionnaire shown in Figure~\ref{img-screenshots} asks whether we already use any Odoo components at our company.
+To start off, the questionnaire shown in Figure~\ref{img-screenshots} asks whether we already use any \textit{Odoo} components at our company.
 If we would have pressed "Yes", we could have chosen which one and in the later steps this would be considered.
-After choosing "No", we are asked which of the Odoo topics interests us, answering it with "Websites" and "Sales".
+After choosing "No", we are asked which of the \textit{Odoo} topics interests us, answering it with "Websites" and "Sales".
 This brings us to a wizard page showing all of the websites we could choose.
 After selecting "eCommerce" the next page already chose "Accounting" for us, as this was one of the dependencies from the features that were selected in the background when we chose "eCommerce".
-No matter what we select on the last page, we can no longer press "next", as there is no next Page for us to configure.
+No matter what we select on the last page, we can no longer press "Next", as there is no next Page for us to configure.
 To get our configuration file we press "Finish", which we could have done any time during the configuration, generating a partial configuration.
@@
 This process could have been done alone with the feature tree, but that would have taken much longer, as there is no sorting and the feature names are not as descriptive as the choices from the questionnaire.
-Although we probably did not cover all possible cases in our questionnaire doe to the lack of domain knowledge, this sample shows that this use case can be handled comfortably with our questionnaire.
-
-%TODO: Auswertung
-
-%Also state how some of the questions and their mapping in the questionnaire were developed.
-
-%Finally, show the process of configuration through running a fictinal user over the questionnaire and document his decisions as well as the resulting configurations.
-
-%TODO: test ausdenken, der alle ``Fähgkeiten'' zeigt
-
-% Fahrradladen, Online-Shop, Social-Media, Bezahldienste, Kontakt-Portal, DE/EN, Newsletter
-%
-% Website builder, eCommerce, SEA
-% Sales, CRM, invoicing, Point of Sale
-% Inventory, Purchase
-% Email Marketing, Survey
-
-%TODO: Planung, durchführung, Auswertung
-
-%TODO: nur ein konstruierter Fall, weil Domain Knowledge fehlt.
+Although we probably did not cover all possible cases in our questionnaire due to the lack of domain knowledge, this sample shows that this use case can be handled comfortably with our questionnaire.
